### 2017-10-06 draft_springer_2.tex
initial commit. submitted version for first deadline

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{cite}
\usepackage{multicol}
%\usepackage{subcaption}

\usepackage{url}
\urldef{\mailsa}\path|Logan.C.Farrell@NASA.gov, Troy.A.Dennis@rice.edu|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Simply Grasping Simple Shapes:\\
Shape Based Synergy Commanding of a Humanoid Hand}

% a short form should be given in case it is too long for the running head
\titlerunning{Simply Grasping Simple Shapes}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Logan C. Farrell$^{1,2}$ %
\and Troy A. Dennis$^{1}$\and Julia Badger$^{2}$\and Marcia K. O'Malley$^{1}$}
%
\authorrunning{Simply Grasping Simple Shapes}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{$^{1}$Mechanical Engineering, Rice University, Houston, TX\\$^{2}$Johnson Space Center, NASA, Houston, TX}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}
Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming the robots to grasp common objects. There exists a need for an efficient method to command high degree of freedom dexterous manipulators for a range of objects such that explicit models are not needed for every interaction. The authors propose a method incorporating the neuroscience concept of synergies to decrease the commanded degrees of freedom to match intuitive measurements of an object, which we term geometrical synergies. Using the SynGrasp toolbox, a model of Robonaut 2’s twelve degree of freedom (DoF) hand was created to perform contact analysis around a small set of cylinders defined by the single variable, diameter. Experiments were performed on the robot to validate and update the synergy-based models.  Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated experimentally. This synergy-based grasp planning method can be applied to any humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs, to grasp commonly shaped objects, vastly multiplying the library of objects able to be manipulated by the robot.
\keywords{Manipulation, grasp, synergy, humanoid, dextrous, hand}
\end{abstract}

\section{Introduction}

Humanoid robots provide the capability to operate in the same space, using the same tools that a human can. The future of these robots can clearly be seen with efforts for robots to go into disaster areas unsafe for humans \cite{fukushima_robots} or help humans do menial tasks. Perhaps the most fundamental capability necessary to accomplish these human tasks is the ability to manipulate the same objects that humans can. For this challenge, many designers have created hands capable of nearly all of the degrees of freedom (DoF) as the human hand \cite{r2_hand}, \cite{DRL}, \cite{hrp3}, \cite{softhand}. However, while the hands are able to form many of the same grips and poses as a human hand, the control of these hands in an intuitive, and simple way has yet to be demonstrated. Until the community can quickly and effectively control these high DoF humanoid hands, robots will still need to be highly specialized for individual tasks. \par
Research shows that humans control their hands not with individual joint position commands, as dexterous robot hands are typically controlled, but instead by a single signal that actuates multiple muscle groups. These groups combine to create the plethora of hand motions humans can form \cite{Santello} \cite{neuro}. This approach gives a method for decreasing the commanded DoF of the hand system to a more manageable number, and is referred to as ``synergies". These synergy schemes still mimic the motions of the human hand, which are difficult to intuitively combine into useful hand motions, shifting the complexity problem from degrees of freedom, to nonintuitive combinations of synergies. \par
The contribution of this paper is a methodology to decrease the commanded DoF from twelve to one for the Robonaut 2 (R2) hand to manipulate simple cylindrical shapes. This methodology replaces all unique cylindrical type models with a single model to allow simple manipulation of common objects. In addition, the single commanded degree of freedom are based on a simple measurement of the object to allow intuitive control. This enables the robot to successfully manipulate any cylindrical object found in its environment with the single model. In addition, this research acheives the objective of evaluating the use and accuracy of SynGrasp simulation in a real-world environment.

\section{Background}

\subsection{Hand Synergies}
	Dexterous manipulation in robots has developed from a simple parallel gripper towards the complexity of the human hand in the past decades. This high DoF system similar to the human hand allows robots to manipulate objects in similar ways to a human. However, as this problem has been studied further, the construction of robotic hands with similar DoFs as the human hand has become common place, but the control is anything but intuitive. The computational costs to calculate the correct closing position around a given object as perceived by a robotic vision system is

$$
f(x) = O(2^N)  \eqno{(1)}
$$
where N represents the number of DoFs, with each DoF controlled individually. Researchers have focused on analyzing the way that humans control our own hands with hopes of extending that same control scheme to a robotic hand, as in the seminal work on postural synergies of human grasping \cite{Santello}.

Neurological studies have demonstrated that the human brain does not plan and execute specific movements of the individual finger joints. Instead, our brain will send high level commands down through the motor cortex to execute sets of actions, and these commands will travel down the spine to activate sets of muscles in combination, rather than just single muscle groups. In this way, our brain is grouping and combining sets of commands in different ways to accomplish the task \cite{neuro}.  Santello's research performed Principal Component Analysis (PCA) on a large range of everyday grasps, and was able to model 50$\%$ of all grasps with a single relationship, or synergy. If a second synergy was added in proportion, roughly 80$\%$  of all grasps could be commanded. Similarly the third synergy resulted in over 90$\%$  of observed grasps. This coupling demonstrates how our brain is potentially reducing the 20 DoF problem of hand motion into only a few DoFs. Thinking in this way greatly reduces the complexity of grasping for humans and allows smooth control of a very large number of DoFs to accomplish grasping  tasks without a large burden on the nervous system.

 Engineers can draw inspiration from this structure to design robotic grasping devices.  A synergistic scheme can be implemented in several ways.  Human hand synergies can be used to identify key DoFs that are necessary for a simplified hand design.  They can also be used to devise under-actuation schemes such as the PISA-IIT soft-hand \cite{softhand}.  Finally, they can be used to simplify the control of fully actuated hands by creating ``Software Synergies" \cite{catalano_2012_adaptive}.

 One of these Software Synergies was demonstrated by Ciorcarlie et al. \cite{ciocarlie_2007_dexterous}.  The group used the GraspIt software to map the two primary human postural synergies to fully actuated robotic hands.  Roa et al. \cite{power_grasp} used a more involved algorithm to study the contacts on complex objects by partitioning the object into planar slices, studying form and force closure  \cite{bicchi} to determine optimal hand closure. An interesting aspect of this approach was it calculated the optimal thumb and index finger closure, and then calculated the remaining fingers to stabilize the grasp.   Garcia et. al. demonstrated how human synergy based motion planning can be used to decrease the computation time for motion planning in humanoid dual arm robot system  \cite{garcia}.

SynGrasp, a MATLAB toolbox developed for the purpose of simulating underactuated robot grasping, is another computational tool based on synergies \cite{syngrasp}.  This toolbox offers three primary capabilities: it allows the user to model robotic hands, perform grasp simulations and analysis, and map synergies on to robot hand designs. We aim to extend this work by using the SynGrasp software, well suited to designing and testing  synergy schemes using kinematics \cite{salvietti_2016_map}.  We also aim to create our own unique purpose-driven synergy scheme instead of attempting to replicate human postural synergies.

The ability to create user defined hand models and synergies makes SynGrasp an ideal tool for simulating a synergy based command structure on R2.  A computational tool for modeling grasps and commands would be hugely beneficial for evaluation of the hand and for designing grips for it.%replace this sentence
While the main purpose of this study is to evaluate a synergy command architecture, it will have the added objective of evaluating the use and accuracy of Syngrasp simulations in real-world environments.

\subsection{Test Platform and Motivation}

NASA is actively developing humanoid robotics to work in the same environment as astronauts. To this end, Robonaut 2 is a humanoid robot with two 7 DoF arms (including the wrist), a 3 DoF neck, 1 DoF waist, two 12 DoF hands, and two 7 DoF legs that is currently on board the International Space Station. The design goal of this robot is to assist astronauts with repetitive tasks on the International Space Station like monitoring airflow, cleaning handrails, and unpacking resupply vehicles \cite{r2_diftler}. Currently, NASA is actively developing technologies to allow this robot to behave with more autonomy. This is necessary to allow supervised control over long time delays as missions progress farther and farther from Earth.

   \begin{figure}[t]
      \centering
      \includegraphics[width=0.4\textwidth]{r2_iss}
      \caption{Robonaut 2 aboard the International Space Station}
      \label{at_r2_iss}
   \end{figure}

To achieve this level of autonomy and dexterity, it becomes intractible to set specific values for each robot joint to form every possible hand pose that R2 might require on board the ISS. Currently, each object to be manipulated must be modeled, the approach trajectories made and tested, and the necessary hand positions made and verified. However, if the commands to control grasps can be decreased from 12 DoF to 1 DoF, this task becomes significantly simpler. Instead of each individual object, a single cylindrical model could be made and verified. Then, the robot will have a model to manipulate any cylindrical object encountered. The application of synergies in this case will save time and effort while increasing the capability and usefulness of the dexterous robot.

\subsection{Current R2 Grasping Process}

In practice, many humanoid systems will use some model based approach to manipulate objects encountered in the world. This can be seen through the DARPA Robotics Competition (DRC) Trials in the ways the teams commanded their humanoids to interact with things like drills, door handles, valves, and other objects. \cite{DRC_Yanco}, \cite{IHMC}. Currently, the R2 project is using the Affordance Templates (AT) framework, initially presented in \cite{affordance_templates}. This system allows a model of an object to be created with different end effector waypoints to create allowable affordances for manipulating the object. Through this AT model, a catalog of different objects with their affordances is created and stored to be used throughout the manipulation process. However, in the current implementation, each new object encountered must have a new Affordance Template created before it can be manipulated. If generic models were available, any new object encountered that fit closely enough to an existing model could be used immediately, with no further development time.

   \begin{figure}[t]
      \centering
      \includegraphics[width=0.6\textwidth]{drill_at2}
      \caption{Robonaut 2 current method for manipulation of a drill using the Affordance Template (AT).  This approach requires a CAD model of the object to be grasped and multiple inputs (grasp position, grasp type) from the user}
      \label{at_example}
   \end{figure}

To create an Affordance Template, the user must first load in the mesh of the object to visualize in the simulated environment as well as give a collision model for motion planning. Next, the user must create different waypoints to dictate the necessary end-effector positions with respect to the object to give the affordance for a manipulation task. There can be multiple affordances per object, for example, a drill could be picked up via the handle or the top, making each approach its own affordance in the template. As part of each waypoint, the end-effector hand pose is dictated. R2;s current grasp library was constructed using the Cutosky Grasp Taxonomy \cite{Cutkosky} and these hand positions form the catalog of available hand poses. If a hand pose is required that is not in this catalog, the user must create a new pose via joint angle commands. The result of this template can be seen in Figure \ref{at_example}. This entire process can take multiple days per object to create and test.

It is readily apparent that this method of manipulation can be time consuming and very application specific. If the robot were to encounter an object slightly outside of the current template, a new template must be made. This will increase design, testing, and verification time to an intractable level for the deep space missions of the future. Instead, the design of single, generic models to be used for similar shapes based on object geometric synergies is proposed. For the cylinder synergies, the same AT framework can be implemented, using a cylindrical mesh corresponding the diameter of the object. Then a standard set of approaches can be saved to approach the open side of the cylinder. Finally, the hand pose can be commanded based on the single DoF of diameter to close around the object. This would allow a flashlight, a coffee cup, a screwdriver, or any other cylinder to be picked up using the same template.

\section{Methods}

\label{methods}

% take this section from 3 paragraphs down to 3 sentences. We basically say all of this somewhere else. 
A synergistic command structure can be mathematically defined in (2).
$$
q = S\sigma  \eqno{(2)}
$$

where q is the vector of joint angles of dimensions [N x 1],  N is the number of synergies, S is the synergy matrix of dimensions [N x M],  M is the number of possible synergies that can be activated and $\sigma$ is the [M x 1] synergy activation vector which determines which synergy or combination thereof is turned on.  The basis of synergies is that the generic joint displacement, q, can be represented as a function of fewer elements than the number of DoFs of the system.  S is a vector of weights that determines the amount of motion for an individual joint resulting from a single input.  In neuroscience, these S matrices are determined by mapping the grasps of various shapes and isolating the movements of individual joints.  The covariances of the various joint angles are analyzed and combined using machine learning to identify when joints are commonly moved in unison, a weighing scalar based on the relative magnitude of motion.  Rather than identifying and isolating synergies from existing behavior as is done in neuroscience, the authors aim to design a synergy by providing an S matrix such that the finger joints move in unison to produce a cylinder grasp.  For this reason, the synergy matrix is designed based on grasp shapes for various sized cylinders.

The objective of this study is to build the commanding infrastructure for R2 to take the inputs of synergy type (e.g. ``cylinder”) and a single variable (e.g. diameter) and calculate the synergy matrix from these two inputs. The q matrix of joint angles will need to then be passed to the robot to command the fingers joints to the calculated angles.

\subsection{SynGrasp Modeling}

\begin{figure}[t]%
\centering
\null\hfill
%\begin{minipage}{1.2in}%
	\subfloat[]{
      \includegraphics[width=0.4\textwidth]{syngrasp_model.jpg}\quad
	}
	\hfill
%     \subcaption{a}
%\end{minipage}%
%\qquad
%\begin{minipage}{0.05in}%
%\end{minipage}%
%\begin{minipage}{1.2in}%
	\subfloat[]{
      \includegraphics[width=0.4\textwidth]{syngrasp_grip_top}}
	\hfill\null
%     \subcaption{b}
%\end{minipage}%

\caption{By matching the finger dimensions and rotation frames, a SynGrasp model of the Robonaut 2 hand was defined (a).  SynGrasp uses a kinematics solver to generate grasps such as those shown in (b). }%
\label{fig:models}%
\end{figure}

The first step is to determine the finger angles for grasps of cylinders of varying diameter using SynGrasp to build an initial model for grasping.  The chosen diameters for grasped objects were 2.54 cm, 3.81 cm, 5.08 cm, and 7.62 cm.  The internal contact model in SynGrasp was used to design the grip.  This performed better than traditional inverse kinematic models because it allowed contact with multiple points on the hand rather than only a single point-of-interest on the end-effector.  The key features such as the number of DoFs, finger length, joint rotation frames, and actuation scheme were matched.  Some areas where the modeling program could not match the actual R2 hand were the compliance of the fingers and the size of the palm.  The Robonaut hand contains 18 movable DoFs but only 12 controllable DoFs.  The thumb is fully controllable along every DoF and contains two DoFs at the basilar joint with independent controls for angle at the proximal phalanx and distal phalanx.  The index and middle fingers have 2 rotation DoFs at the metacarpophalangeal joint (MCP), pitch and yaw.  The proximal (PIP) and distal (DIP) interphalangeal joints are underactuated such that they move at matching angles.  The ring and little fingers only take a single input value that controls pitch in all three joints (MCP, PIP, and DIP).  These two fingers have no yawing DoF at the MCP.  The SynGrasp model was provided a synergy matrix to reflect this scheme and grips were designed to include these constraints.

%TODO: Add figure of R2 hand back in here to show DoF

\subsection{Testing Method} 
A simple testing method was used to both validate the models, as well as perform the final experiments to determine grasp efficacy. A cylindrical object was placed on the table, touching R2's open palm. The object's placement along the palm was varied from near the base of the fingers to the base of the thumb. This allowed testing of uncertainty in position that will be present when the object must be localized. Then, the robot was commanded to close its hand based on the synergy values, lift the object, rotate the object upside down, return it to straight, and finally, release it back on the table. This set of motions demonstrates a firm grasp on the object through a large motion of the robot.

\begin{figure}[]
  \centering
  \includegraphics[width=\linewidth]{manipulation}
  \caption{Manipulation action taken by R2 to determine successful grasps}
  \label{testing}
\end{figure}

\subsection{Model Refinement and Synergy Development}
The models were validated by commanding R2's hand to close around a cylindrical piece of aluminum exactly equal to our modeled diameter using the values dictated by Syngrasp. The grasps were tested and refined using the previously mentioned test method and the model discrepancies were accounted for. These discrepancies are discussed in detail in Section \ref{discussion}. Once the final values from testing were established, the four positions for each finger were plotted and a polynomial fit to the data was carried out. The fits were calculated so that the maximum error for each data point was 4 degrees.   The maximum order used was three, however, many of the joints required lower orders. The resulting relationships were relatively simple which intuitively makes sense. As the object gets larger, the hand opens more. The thumb is the only digit which changed orientations substantially as the diameters got larger as it has more DoF to move into a suitable position. The graph of the thumb joint angle fits was presented in Fig. \ref{thumb_fits}.

\begin{figure}[!b]
  \centering
  \includegraphics[width=1.08\linewidth]{Thumb_Fits_2}
  \caption{Thumb joint angles when grasping cylinders of varying diameter.  The curve fit shows interpolation between collected data points.}
  \label{thumb_fits} 
\end{figure}

\begin{figure*}[!b]
  \centering
  \includegraphics[width=1.08\linewidth]{Objects3.pdf}
  \caption{Results from cylindrical synergy testing using the developed curve fits.  The blue field contrains the pure cylindrical objects.  The orange contains rectangular prisms, and the yellow contains the only complex geometry object, the drill}
  \label{objects} 
\end{figure*}

\section{RESULTS}
\label{results}

After model validation on the robot and subsequent adjustments, the robot was able to manipulate fifteen objects in the experiment using the single synergy commanding structure. In addition, five non-cylindrical objects were tested that demonstrated the applicability of this synergy to more than pure cylinders as well as the cases in which this method is not applicable.

\subsection{Synergy Testing}

Twenty common objects found in a laboratory setting were tested to validate the effectiveness of the curve fits creating the synergy. The list of these objects as well as their success can be viewed in Fig. \ref{objects}.  Of the 20 objects manipulated, 17 were manipulated with no issues, 1 slipped in the grip, and 2 were dropped outright.

Of the objects selected and tested, 15 could be considered pure cylinders. Of these cylinders, the only one not successfully manipulated at all was the large flashlight. This object slid out of the robot's grasp as it was manipulated. A qualitative evaluation of the grasp suggested the fingers were in an appropriate position.The flashlight was the heaviest object manipulated by the robot (1 kg) and the friction that the robot could apply through the normal force and the glove material was inadequate to manipulate it. The authors believe this is not achievable by the robot regardless of the method of grasp determination. In addition, the robot did not maintain a firm grasp on the hammer. The hammer shank diameter is at the small end of the range that the robot is able to grasp even with a full hand close position due the kinematics of the hand joints and the friction of the glove. The hammer slid in the grasp, but was not dropped. In practice, R2 would be able to manipulate this object to a new location. R2 maintained solid control of the object for all the other cylinders.

Four prismatic objects were tested in to understand the model applicability outside of a pure cylinder. The robot succeeded in manipulating each of these four objects. This suggests that this grasp abstracts to more than cylinders, instead, it could be considered a power grasp synergy based on the Cutkosky Grasps, further generalizing the theory.

Finally, the tested synergy was unable to grasp the Dewalt impact driver. As the robot closed its hand, the index finger caught on the trigger, not allowing the hand to fully wrap around the handle. Upon the rotation action, the Dewalt was dropped. This shows that while the synergy concept is useful, it is not directly applicable to all cases and gives an indication of the usefulness of individually actuated joints.

\section{Discussion}
\label{discussion}

Through the testing, the synergy model proposed successfully manipulated all of the cylindrical objects presented in the experiment, demonstrating the usefulness of the concept in practice. The testing also highlighted the further abstraction of the grasp for a cylinder synergy to a power grasp synergy through the manipulation of the prismatic objects. Finally, it was demonstrated that while this synergy is useful for cylinders, additional hand DoFs are still necessary for complex manipulations like that of a drill.

%\subsection{SynGrasp Model Validation}

The SynGrasp model provided a very useful method to determine a starting point for grasp refinement. The SynGrasp model remains, an idealized model of the robot hand. Many aspects could not be accurately modeled and had to be adjusted through the model validation process, as discussed below. Future additions to the software to allow more realistic actuation could include friction models and more control over the geometry of the hand, as R2's palm is larger than the model allowed. Going forward, SynGrasp is useful for other synergy types such as pinch grasp which has contact forces only in the fingers and does not require use of the palm.

\begin{figure}[!b]
\centering
\null\hfill
  %\begin{minipage}{2in}
	\subfloat[]{
     	 \includegraphics[width=0.45\textwidth]{pinky_out_crop}}\quad
	\hfill
%      \subcaption{a}
 % \end{minipage}%
 % \begin{minipage}{2in}
	\subfloat[]{
      \includegraphics[width=0.45\textwidth]{pinky_in_crop}}
	\hfill\null
 %     \subcaption{b}
  %\end{minipage}
  \caption{Initial (a) and final (b) joint angles for ring and little fingers. The initial round of testing following SynGrasp model generation resulted in no contact in the ring and little fingers.  This result in due to tendon friction in the actual system that reduced the closure angle to a lower value than commanded.}%
\label{pinkymodels}%
\end{figure}

The SynGrasp model assumes the friction among multiple joints actuated with a single tendon is equal, allowing all of the joints to move in unison. However, in practice this is not the case. On the R2 hand, especially on the ring and little fingers, the first joint will move exclusively until it comes into contact with the object, then the next joints will begin to actuate. This resulted in poor finger placement for the ring and little fingers on initial model validation and the closing values had to be increased to obtain a firm grip using those fingers. The result of this can be seen in Fig. \ref{pinkymodels}

In addition, the 4 DoF thumb has many possible locations in which it could contact the cylinder in Syngrasp, and due to the redundant DoF, the thumb location choice performed poorly for larger objects near 7.62 cm diameter. Primarily, the thumb would roll too close to the palm, giving a point contact on the thumb pad for larger diameters rather than a wrap around the cylinder. The thumb position was adjusted via testing. The index and middle finger values still proved valid.

A result from the grasping tests was that cylinders near 10 cm were grasped by the robot in a pinch grasp fashion due to the size, so a future pinch grasp model could incorporate larger objects. Also, the geometric synergy method was unable to handle the complex geometry of the drill, which demonstrates that while the synergy concept is useful, it is not directly applicable to all cases and gives an indication of the usefulness of individually actuated joints. Typical manipulation of this tool has the index finger extended, allowing the other fingers to wrap underneath using the synergy-based cylinder grasp values. This could be achieved with a second synergy in combination with the cylinder synergy that weights the extension of the index finger. The combination of these two synergies could create the Dewalt drill grasp and actuation motions in the same framework. This is a concept the authors are leaving for future work.

%\subsection{Ease of Use}

%Through this work, the authors conjecture that while previous approaches have sufficiently modeled the hand motions similar to a human, there has been no framework for modeling grasp motions intuitive to a robot user. Santello's work exposed the usefulness of decomposing hand motions into synergies to allow for control on a lower DoF, however, this results in a different control problem to combine non-intuitive motions. Other works use online planning and an accurate object model to determine the appropriate grasp which creates the need for very accurate models or sensors as well as online computational time. The system proposed creates a simple and intuitive model for grasping. Once generated, this model requires effectively no online computation and can be executed with a single, easily understood, user input.

%\subsection{Applicability and Future Work}

%The approach demonstrated in this work shows a useful method of grasping objects commonly manipulated through a power grasp. There is a simple logical step to then apply these methods to determine the synergies for other types of grasp such as a pinch grasp or ball grasp, and effectively change the Cutkosky grasps from single shapes, to sets of relationships. However, to truly do human type manipulation, the individually commanded DoF must remain as shown with the Dewalt drill manipulation. This type of manipulation could be captured in this framework via an additional synergy focused on the position of the index finger. These simple additions could allow individual finger actions that are still intuitive to program to be added to the overall hand motions that have been demonstrated to work.

\section{CONCLUSIONS}

The authors demonstrated a novel concept to incorporate the synergy framework developed in neuroscience and analyzed in practice  into an intuitive commanding strategy for a high DoF robot hand on Robonaut 2. The creation of a synergy based on the diameter of a cylindrical object allowed cylinders of varying sizes to be effectively grasped via a single command input. The results of this test suggest that this concept could be used to quickly broaden the library of objects the robot can manipulate from a small, specialized set, into a nearly infinite library of manipulatable cylinders.

\bibliographystyle{splncs}

\bibliography{BibFile}

\end{document}

### 2017-10-10 draft_springer_2.tex
Updated to include the small changes given by the thrid reviewer

@@
 \title{Simply Grasping Simple Shapes:\\
-Shape Based Synergy Commanding of a Humanoid Hand}
+Commanding a Humanoid Hand with a Shape-Based Synergy}
 
@@
 % unless you accept that it will be published
-\institute{$^{1}$Mechanical Engineering, Rice University, Houston, TX\\$^{2}$Johnson Space Center, NASA, Houston, TX}
+\institute{$^{1}$Mechanical Engineering, Rice University, Houston, USA\\$^{2}$Johnson Space Center, NASA, Houston, USA}
 
@@
 \begin{abstract}
-Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming the robots to grasp common objects.
-There exists a need for an efficient method to command high degree of freedom dexterous manipulators for a range of objects such that explicit models are not needed for every interaction.
-The authors propose a method incorporating the neuroscience concept of synergies to decrease the commanded degrees of freedom to match intuitive measurements of an object, which we term geometrical synergies.
-Using the SynGrasp toolbox, a model of Robonaut 2’s twelve degree of freedom (DoF) hand was created to perform contact analysis around a small set of cylinders defined by the single variable, diameter.
+Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming robots to grasp common objects.
+There exists a need for an efficient method to command high degree-of-freedom (DoF) dexterous manipulators for a range of objects such that explicit models are not needed for every interaction.
+The authors propose a method incorporating the neuroscience concept of synergies to decrease the commanded DoFs to match intuitive measurements of an object, which we term geometrical synergies.
+Using the SynGrasp toolbox, a model of Robonaut 2`s twelve-DoF hand was created to perform contact analysis around a small set of cylinders defined by a single variable, diameter.
 Experiments were performed on the robot to validate and update the synergy-based models.
 Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated experimentally.
-This synergy-based grasp planning method can be applied to any humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs, to grasp commonly shaped objects, vastly multiplying the library of objects able to be manipulated by the robot.
-\keywords{Manipulation, grasp, synergy, humanoid, dextrous, hand}
+This synergy-based grasp planning method can be applied to any humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs, to grasp commonly shaped objects, vastly multiplying the library of objects the robot can manipulate.
+\keywords{Manipulation, grasp, synergy, humanoid, dexterous, hand}
 \end{abstract}
@@
 Perhaps the most fundamental capability necessary to accomplish these human tasks is the ability to manipulate the same objects that humans can.
-For this challenge, many designers have created hands capable of nearly all of the degrees of freedom (DoF) as the human hand \cite{r2_hand}, \cite{DRL}, \cite{hrp3}, \cite{softhand}.
+For this challenge, many designers have created hands capable of nearly all of the DoFs as the human hand \cite{r2_hand}, \cite{DRL}, \cite{hrp3}, \cite{softhand}.
 However, while the hands are able to form many of the same grips and poses as a human hand, the control of these hands in an intuitive, and simple way has yet to be demonstrated.
@@
 This approach gives a method for decreasing the commanded DoF of the hand system to a more manageable number, and is referred to as ``synergies".
-These synergy schemes still mimic the motions of the human hand, which are difficult to intuitively combine into useful hand motions, shifting the complexity problem from degrees of freedom, to nonintuitive combinations of synergies.
+These synergy schemes represen the principle components of various grasps of the human hand.
+These components can be difficult to intuitively combine into useful hand motions, shifting the complexity problem from DoF, to nonintuitive combinations of synergies.
 \par
@@
 This methodology replaces all unique cylindrical type models with a single model to allow simple manipulation of common objects.
-In addition, the single commanded degree of freedom are based on a simple measurement of the object to allow intuitive control.
+In addition, the single commanded DoF is based on a simple measurement of the object to allow intuitive control.
 This enables the robot to successfully manipulate any cylindrical object found in its environment with the single model.
-In addition, this research acheives the objective of evaluating the use and accuracy of SynGrasp simulation in a real-world environment.
 
@@
 	Dexterous manipulation in robots has developed from a simple parallel gripper towards the complexity of the human hand in the past decades.
-This high DoF system similar to the human hand allows robots to manipulate objects in similar ways to a human.
+These devices are high DoF systemsthat allow robots to manipulate objects in similar ways to a human.
 However, as this problem has been studied further, the construction of robotic hands with similar DoFs as the human hand has become common place, but the control is anything but intuitive.
-The computational costs to calculate the correct closing position around a given object as perceived by a robotic vision system is
-
-$$
-f(x) = O(2^N)  \eqno{(1)}
-$$
+The computational costs to calculate the correct closing position around a given object as perceived by a robotic vision system is $O(2^N)$
  where N represents the number of DoFs, with each DoF controlled individually.
@@
 In this way, our brain is grouping and combining sets of commands in different ways to accomplish the task \cite{neuro}.
-Santello's research performed Principal Component Analysis (PCA) on a large range of everyday grasps, and was able to model 50$\%$ of all grasps with a single relationship, or synergy.
-If a second synergy was added in proportion, roughly 80$\%$  of all grasps could be commanded.
-Similarly the third synergy resulted in over 90$\%$  of observed grasps.
+Santello et al.
+performed Principal Component Analysis (PCA) on a large range of everyday grasps, and was able to model 50$\%$ of the variability in the grasps with a single relationship, or synergy.
+If a second synergy was added in proportion, roughly 80$\%$  of the variability in grasps could be commanded.
+Similarly the third synergy resulted in modeling 90$\%$  of observed grasp variability.
 This coupling demonstrates how our brain is potentially reducing the 20 DoF problem of hand motion into only a few DoFs.
@@
 This toolbox offers three primary capabilities: it allows the user to model robotic hands, perform grasp simulations and analysis, and map synergies on to robot hand designs.
-We aim to extend this work by using the SynGrasp software, well suited to designing and testing  synergy schemes using kinematics \cite{salvietti_2016_map}.
+SynGrasp is well suited to designing and testing  synergy schemes using kinematics \cite{salvietti_2016_map}.
 We also aim to create our own unique purpose-driven synergy scheme instead of attempting to replicate human postural synergies.
 
-The ability to create user defined hand models and synergies makes SynGrasp an ideal tool for simulating a synergy based command structure on R2.
-A computational tool for modeling grasps and commands would be hugely beneficial for evaluation of the hand and for designing grips for it.%replace this sentence
-While the main purpose of this study is to evaluate a synergy command architecture, it will have the added objective of evaluating the use and accuracy of Syngrasp simulations in real-world environments.
+The ability to create user-defined hand models and synergies makes SynGrasp an ideal tool for simulating a synergy based command structure on R2.
+A computational tool for modeling grasps and commands would be hugely beneficial for evaluation of the hand and for designing grips for it.
+%replace this sentence
+While the main purpose of this study is to evaluate a synergy command architecture, it will have the added objective of evaluating the use and accuracy of SynGrasp simulations in real-world environments.
 
@@
 NASA is actively developing humanoid robotics to work in the same environment as astronauts.
-To this end, Robonaut 2 is a humanoid robot with two 7 DoF arms (including the wrist), a 3 DoF neck, 1 DoF waist, two 12 DoF hands, and two 7 DoF legs that is currently on board the International Space Station.
+To this end, Robonaut 2 is a humanoid robot with two 7 DoF arms (including the wrist), a 3 DoF neck, 1 DoF waist, two 12 DoF hands, and two 7 DoF legs.
+This robot is currently on board the International Space Station.
 The design goal of this robot is to assist astronauts with repetitive tasks on the International Space Station like monitoring airflow, cleaning handrails, and unpacking resupply vehicles \cite{r2_diftler}.
@@
 As part of each waypoint, the end-effector hand pose is dictated.
-R2;s current grasp library was constructed using the Cutosky Grasp Taxonomy \cite{Cutkosky} and these hand positions form the catalog of available hand poses.
+R2`s current grasp library was constructed using the Cutosky Grasp Taxonomy \cite{Cutkosky} and these hand positions form the catalog of available hand poses.
 If a hand pose is required that is not in this catalog, the user must create a new pose via joint angle commands.
@@
 Instead, the design of single, generic models to be used for similar shapes based on object geometric synergies is proposed.
-For the cylinder synergies, the same AT framework can be implemented, using a cylindrical mesh corresponding the diameter of the object.
+For the cylinder synergies, the same AT framework can be implemented, using a cylindrical mesh corresponding to the diameter of the object.
 Then a standard set of approaches can be saved to approach the open side of the cylinder.
@@
 
-where q is the vector of joint angles of dimensions [N x 1],  N is the number of synergies, S is the synergy matrix of dimensions [N x M],  M is the number of possible synergies that can be activated and $\sigma$ is the [M x 1] synergy activation vector which determines which synergy or combination thereof is turned on.
-The basis of synergies is that the generic joint displacement, q, can be represented as a function of fewer elements than the number of DoFs of the system.
-S is a vector of weights that determines the amount of motion for an individual joint resulting from a single input.
-In neuroscience, these S matrices are determined by mapping the grasps of various shapes and isolating the movements of individual joints.
+where $q$ is the vector of joint angles of dimensions [$N*1$],  $N$ is the number of synergies, $S$ is the synergy matrix of dimensions [$N*M$],  $M$ is the number of possible synergies that can be activated and $\sigma$ is the [$M *1$] synergy activation vector which determines which synergy or combination thereof is turned on.
+The basis of synergies is that the generic joint displacement, $q$, can be represented as a function of fewer elements than the number of DoFs of the system.
+$S$ is a vector of weights that determines the amount of motion for an individual joint resulting from a single input.
+In neuroscience, these $S$ matrices are determined by mapping the grasps of various shapes and isolating the movements of individual joints.
 The covariances of the various joint angles are analyzed and combined using machine learning to identify when joints are commonly moved in unison, a weighing scalar based on the relative magnitude of motion.
-Rather than identifying and isolating synergies from existing behavior as is done in neuroscience, the authors aim to design a synergy by providing an S matrix such that the finger joints move in unison to produce a cylinder grasp.
+Rather than identifying and isolating synergies from existing behavior as is done in neuroscience, the authors aim to design a synergy by providing an $S$ matrix such that the finger joints move in unison to produce a cylinder grasp.
 For this reason, the synergy matrix is designed based on grasp shapes for various sized cylinders.
@@
 \subsection{Testing Method} 
-A simple testing method was used to both validate the models, as well as perform the final experiments to determine grasp efficacy.
+A simple testing method was used to validate the models, as well as perform the final experiments to determine grasp efficacy.
 A cylindrical object was placed on the table, touching R2's open palm.
@@
 \subsection{Model Refinement and Synergy Development}
-The models were validated by commanding R2's hand to close around a cylindrical piece of aluminum exactly equal to our modeled diameter using the values dictated by Syngrasp.
+The models were validated by commanding R2's hand to close around a cylindrical piece of aluminum exactly equal to our modeled diameter using the values dictated by SynGrasp.
 The grasps were tested and refined using the previously mentioned test method and the model discrepancies were accounted for.
 These discrepancies are discussed in detail in Section \ref{discussion}.
-Once the final values from testing were established, the four positions for each finger were plotted and a polynomial fit to the data was carried out.
+Once the final values from testing were established, the results from each cylinder diameter for each finger were plotted and a polynomial fit to the data was carried out.
 The fits were calculated so that the maximum error for each data point was 4 degrees.
@@
 The thumb is the only digit which changed orientations substantially as the diameters got larger as it has more DoF to move into a suitable position.
-The graph of the thumb joint angle fits was presented in Fig.
+The graph of the thumb joint angle fits are shown in Fig.
 \ref{thumb_fits}.
@@
 This object slid out of the robot's grasp as it was manipulated.
-A qualitative evaluation of the grasp suggested the fingers were in an appropriate position.The flashlight was the heaviest object manipulated by the robot (1 kg) and the friction that the robot could apply through the normal force and the glove material was inadequate to manipulate it.
+A qualitative evaluation of the grasp suggested the fingers were in an appropriate position.
+The flashlight was the heaviest object manipulated by the robot (1 kg) and the friction that the robot could apply through the normal force and the glove material was inadequate to manipulate it.
 The authors believe this is not achievable by the robot regardless of the method of grasp determination.
@@
 
-Four prismatic objects were tested in to understand the model applicability outside of a pure cylinder.
+Four prismatic objects were tested to understand the model applicability outside of a pure cylinder.
 The robot succeeded in manipulating each of these four objects.
@@
 The SynGrasp model provided a very useful method to determine a starting point for grasp refinement.
-The SynGrasp model remains, an idealized model of the robot hand.
+The SynGrasp model remains an idealized model of the robot hand.
 Many aspects could not be accurately modeled and had to be adjusted through the model validation process, as discussed below.
@@
 
-In addition, the 4 DoF thumb has many possible locations in which it could contact the cylinder in Syngrasp, and due to the redundant DoF, the thumb location choice performed poorly for larger objects near 7.62 cm diameter.
+In addition, the 4 DoF thumb has many possible locations in which it could contact the cylinder in SynGrasp, and due to the redundant DoF, the thumb location choice performed poorly for larger objects near 7.62 cm diameter.
 Primarily, the thumb would roll too close to the palm, giving a point contact on the thumb pad for larger diameters rather than a wrap around the cylinder.

### 2017-10-11 draft_springer_2.tex
updated abstract, reorganized results and discussion

@@
 There exists a need for an efficient method to command high degree-of-freedom (DoF) dexterous manipulators for a range of objects such that explicit models are not needed for every interaction.
-The authors propose a method incorporating the neuroscience concept of synergies to decrease the commanded DoFs to match intuitive measurements of an object, which we term geometrical synergies.
+The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoFs to match intuitive measurements of an object, which we term geometrical synergies.
+The approach of this paper is similar to that of Ciocarlie et al.
+\cite{ciocarlieallen}, however, rather than testing the postural synergies that come from the principle components of a human grasps, the authors design a grasping synergy based on the object that is meant to be grasped.
+For this paper, the synergy was designed to grasp cylinder-shaped objects.
 Using the SynGrasp toolbox, a model of Robonaut 2`s twelve-DoF hand was created to perform contact analysis around a small set of cylinders defined by a single variable, diameter.
 Experiments were performed on the robot to validate and update the synergy-based models.
-Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated experimentally.
+Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated in a proof-of-concept experiment.
 This synergy-based grasp planning method can be applied to any humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs, to grasp commonly shaped objects, vastly multiplying the library of objects the robot can manipulate.
@@
 In practice, many humanoid systems will use some model based approach to manipulate objects encountered in the world.
-This can be seen through the DARPA Robotics Competition (DRC) Trials in the ways the teams commanded their humanoids to interact with things like drills, door handles, valves, and other objects.
+This can be seen through the DARPA Robotics Challenge (DRC) Trials in the ways the teams commanded their humanoids to interact with things like drills, door handles, valves, and other objects.
 \cite{DRC_Yanco}, \cite{IHMC}.
@@
 A cylindrical object was placed on the table, touching R2's open palm.
+All fingers were fully extended in the starting position.
 The object's placement along the palm was varied from near the base of the fingers to the base of the thumb.
@@
 
+\section{Discussion}
+\label{discussion}
+
 Of the objects selected and tested, 15 could be considered pure cylinders.
@@
 This shows that while the synergy concept is useful, it is not directly applicable to all cases and gives an indication of the usefulness of individually actuated joints.
-
-\section{Discussion}
-\label{discussion}
 

### 2017-10-11 draft_springer_2.tex
reworked the Current R2 Grasping section to de-emphasize AT and give a brief discription of the finger control

@@
 
-In practice, many humanoid systems will use some model based approach to manipulate objects encountered in the world.
-This can be seen through the DARPA Robotics Challenge (DRC) Trials in the ways the teams commanded their humanoids to interact with things like drills, door handles, valves, and other objects.
-\cite{DRC_Yanco}, \cite{IHMC}.
-Currently, the R2 project is using the Affordance Templates (AT) framework, initially presented in \cite{affordance_templates}.
-This system allows a model of an object to be created with different end effector waypoints to create allowable affordances for manipulating the object.
-Through this AT model, a catalog of different objects with their affordances is created and stored to be used throughout the manipulation process.
-However, in the current implementation, each new object encountered must have a new Affordance Template created before it can be manipulated.
-If generic models were available, any new object encountered that fit closely enough to an existing model could be used immediately, with no further development time.
+R2's command structure centers around the concept of multi-loop control with a progressive series of loops \cite{r2_control}.
+The lowest level of control is a current loop, wrapped by a velocity loop, wrapped by a torque loop, and finally wrapped by a position loop that the user is dictating.
+However, the R2 finger actuators are not series elastic and have no direct torque measurement.
+Therefore, the torque loop is removed in the multi-loop control model and current limiting is placed at the lowest level to protect the finger tendons.
+This loop structure eliminates the capability to do direct torque control of the fingers to close around an object.
+This dictates the need for a position control scheme to command the hand to manipulate objects.
 
@@
 
-To create an Affordance Template, the user must first load in the mesh of the object to visualize in the simulated environment as well as give a collision model for motion planning.
-Next, the user must create different waypoints to dictate the necessary end-effector positions with respect to the object to give the affordance for a manipulation task.
-There can be multiple affordances per object, for example, a drill could be picked up via the handle or the top, making each approach its own affordance in the template.
-As part of each waypoint, the end-effector hand pose is dictated.
-R2`s current grasp library was constructed using the Cutosky Grasp Taxonomy \cite{Cutkosky} and these hand positions form the catalog of available hand poses.
-If a hand pose is required that is not in this catalog, the user must create a new pose via joint angle commands.
-The result of this template can be seen in Figure \ref{at_example}.
-This entire process can take multiple days per object to create and test.
+Due to this position control scheme, the original grasp process used by R2 was based on the Cutkosky Grasp Taxonomy \cite{Cutkosky}.
+This series of 24 position defined grasps composed the main method of manipulating an object in conjunction with the Affordance Template Framework \cite{affordance_templates} similar to systems used on other humanoid robots \cite{DRC_Yanco}, \cite{IHMC}.
+However, each of these templates, an example of which is shown in Fig \ref{at_example}, is unique to the object using one of the Cutcosky grasps.
+If a new grasp is needed, it must be created, tested and verified.
+If a new object that is slightly different than a current known object is encountered, a new Affordance Template and grasp must be created and tested.
 
-It is readily apparent that this method of manipulation can be time consuming and very application specific.
-If the robot were to encounter an object slightly outside of the current template, a new template must be made.
-This will increase design, testing, and verification time to an intractable level for the deep space missions of the future.
-Instead, the design of single, generic models to be used for similar shapes based on object geometric synergies is proposed.
-For the cylinder synergies, the same AT framework can be implemented, using a cylindrical mesh corresponding to the diameter of the object.
-Then a standard set of approaches can be saved to approach the open side of the cylinder.
-Finally, the hand pose can be commanded based on the single DoF of diameter to close around the object.
-This would allow a flashlight, a coffee cup, a screwdriver, or any other cylinder to be picked up using the same template.
+This creation of templates and gasp positoins can be time consuming and very application specific and is intractable at a large scale for robots in practice.
+In addition, the current proposed methods of using the synergies based on the PCA of the human hand are equally non-intuitve to program in a position based scheme.
+Therefore, a commanding structure to determine hand position based on simple properties of the object is proposed.
+Specifically for this work, the authors propose a geometric synergy based on cylindrical type objects.
+The finger position can be commanded based on the single DoF dictated by the diamter of the object.
+This would allow a flashlight, a coffee cup, a screwdrirver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter.
 

### 2017-10-16 draft_springer_2.tex
so, for some reason, it says I deleted everything and re-wrote it. I didn't I fixed some wordings, reworked some ares. I put the sections back into discussion and flipped them around. I think its more clear. I consolodated results down to 1 section.

@@
 This synergy-based grasp planning method can be applied to any humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs, to grasp commonly shaped objects, vastly multiplying the library of objects the robot can manipulate.
-\keywords{Manipulation, grasp, synergy, humanoid, dexterous, hand}
+\keywords{Manipulation, Grasp, Synergy, Humanoid, Dexterous Hand}
 \end{abstract}
@@
 For this challenge, many designers have created hands capable of nearly all of the DoFs as the human hand \cite{r2_hand}, \cite{DRL}, \cite{hrp3}, \cite{softhand}.
-However, while the hands are able to form many of the same grips and poses as a human hand, the control of these hands in an intuitive, and simple way has yet to be demonstrated.
+However, while the hands are able to form many of the same grips and poses as a human hand, the control of these hands in an intuitive and simple way has yet to be demonstrated.
 Until the community can quickly and effectively control these high DoF humanoid hands, robots will still need to be highly specialized for individual tasks.
@@
 This approach gives a method for decreasing the commanded DoF of the hand system to a more manageable number, and is referred to as ``synergies".
-These synergy schemes represen the principle components of various grasps of the human hand.
+These synergy schemes represent the principle components of various grasps of the human hand.
 These components can be difficult to intuitively combine into useful hand motions, shifting the complexity problem from DoF, to nonintuitive combinations of synergies.
@@
 	Dexterous manipulation in robots has developed from a simple parallel gripper towards the complexity of the human hand in the past decades.
-These devices are high DoF systemsthat allow robots to manipulate objects in similar ways to a human.
+These devices are high DoF systems that allow robots to manipulate objects in similar ways to a human.
 However, as this problem has been studied further, the construction of robotic hands with similar DoFs as the human hand has become common place, but the control is anything but intuitive.
@@
 To this end, Robonaut 2 is a humanoid robot with two 7 DoF arms (including the wrist), a 3 DoF neck, 1 DoF waist, two 12 DoF hands, and two 7 DoF legs.
-This robot is currently on board the International Space Station.
+R2 is currently on board the International Space Station.
 The design goal of this robot is to assist astronauts with repetitive tasks on the International Space Station like monitoring airflow, cleaning handrails, and unpacking resupply vehicles \cite{r2_diftler}.
@@
 \subsection{Current R2 Grasping Process}
-
+REWRITTEN SECTION 
 R2's command structure centers around the concept of multi-loop control with a progressive series of loops \cite{r2_control}.
@@
 Therefore, the torque loop is removed in the multi-loop control model and current limiting is placed at the lowest level to protect the finger tendons.
-This loop structure eliminates the capability to do direct torque control of the fingers to close around an object.
-This dictates the need for a position control scheme to command the hand to manipulate objects.
+This loop structure eliminates the capability to do direct torque control of the fingers to close around an object, thus dictating the need for a position control scheme to command the hand to manipulate objects.
 
@@
 Due to this position control scheme, the original grasp process used by R2 was based on the Cutkosky Grasp Taxonomy \cite{Cutkosky}.
-This series of 24 position defined grasps composed the main method of manipulating an object in conjunction with the Affordance Template Framework \cite{affordance_templates} similar to systems used on other humanoid robots \cite{DRC_Yanco}, \cite{IHMC}.
-However, each of these templates, an example of which is shown in Fig \ref{at_example}, is unique to the object using one of the Cutcosky grasps.
+This series of 24 position defined grasps composed the main method of grasping an object.
+For full manipulation, the CutKosky grasps are used in conjunction with the Affordance Template Framework \cite{affordance_templates}.
+This implementation is similar to systems used on other humanoid robots \cite{DRC_Yanco}, \cite{IHMC}.
+However, each of these templates is unique to the object using one of the Cutcosky grasps.
+An example Affordance Template is shown in Fig \ref{at_example}.
 If a new grasp is needed, it must be created, tested and verified.
@@
 
-This creation of templates and gasp positoins can be time consuming and very application specific and is intractable at a large scale for robots in practice.
-In addition, the current proposed methods of using the synergies based on the PCA of the human hand are equally non-intuitve to program in a position based scheme.
+This creation of templates and gasp positions can be time consuming and very application specific and is intractable at a large scale for robots in practice.
+In addition, the current proposed methods of using the synergies based on the PCA of the human hand are equally non-intuitive to program in a position based scheme.
 Therefore, a commanding structure to determine hand position based on simple properties of the object is proposed.
 Specifically for this work, the authors propose a geometric synergy based on cylindrical type objects.
-The finger position can be commanded based on the single DoF dictated by the diamter of the object.
-This would allow a flashlight, a coffee cup, a screwdrirver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter.
-
+The finger position can be commanded based on the single DoF dictated by the diameter of the object.
+This would allow a flash light, a coffee cup, a screwdriver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter.
+END REWRITTEN SECTION
 \section{Methods}
@@
 % take this section from 3 paragraphs down to 3 sentences. We basically say all of this somewhere else. 
-A synergistic command structure can be mathematically defined in (2).
+A synergistic command structure can be mathematically defined in (1).
 $$
-q = S\sigma  \eqno{(2)}
+q = S\sigma  \eqno{(1)}
 $$
-
-where $q$ is the vector of joint angles of dimensions [$N*1$],  $N$ is the number of synergies, $S$ is the synergy matrix of dimensions [$N*M$],  $M$ is the number of possible synergies that can be activated and $\sigma$ is the [$M *1$] synergy activation vector which determines which synergy or combination thereof is turned on.
+where $q$ is the vector of joint angles of dimensions [$N \times 1$],  $N$ is the number of synergies, $S$ is the synergy matrix of dimensions [$N \times M$],  $M$ is the number of possible synergies that can be activated and $\sigma$ is the [$M \times 1$] synergy activation vector which determines which synergy or combination thereof is turned on.
 The basis of synergies is that the generic joint displacement, $q$, can be represented as a function of fewer elements than the number of DoFs of the system.
@@
 In neuroscience, these $S$ matrices are determined by mapping the grasps of various shapes and isolating the movements of individual joints.
-The covariances of the various joint angles are analyzed and combined using machine learning to identify when joints are commonly moved in unison, a weighing scalar based on the relative magnitude of motion.
-Rather than identifying and isolating synergies from existing behavior as is done in neuroscience, the authors aim to design a synergy by providing an $S$ matrix such that the finger joints move in unison to produce a cylinder grasp.
+The covariances of the various joint angles are analyzed and combined using machine learning to identify when joints are commonly moved in unison, a weighting scalar based on the relative magnitude of motion.
+Rather than identifying and isolating synergies from existing behaviour as is done in neuroscience, the authors aim to design a synergy by providing an $S$ matrix such that the finger joints move in unison to produce a cylinder grasp.
 For this reason, the synergy matrix is designed based on grasp shapes for various sized cylinders.
@@
 The maximum order used was three, however, many of the joints required lower orders.
-The resulting relationships were relatively simple which intuitively makes sense.
-As the object gets larger, the hand opens more.
+The resulting relationships were relatively simple which intuitively makes sense, as the object gets larger, the hand opens more.
 The thumb is the only digit which changed orientations substantially as the diameters got larger as it has more DoF to move into a suitable position.
@@
 
-After model validation on the robot and subsequent adjustments, the robot was able to manipulate fifteen objects in the experiment using the single synergy commanding structure.
-In addition, five non-cylindrical objects were tested that demonstrated the applicability of this synergy to more than pure cylinders as well as the cases in which this method is not applicable.
-
-\subsection{Synergy Testing}
-
-Twenty common objects found in a laboratory setting were tested to validate the effectiveness of the curve fits creating the synergy.
+REWRITTEN
+After model validation on the robot and subsequent adjustments, the robot was able to manipulate 13 of 15 cylindrical objects in the experiment using the single synergy commanding structure.
+In addition, five non-cylindrical objects were tested, four of which were nearly square rectangular prisms, and one drill.
+All four rectangular prism objects were successfully grasped which demonstrated the applicability of this synergy to more than pure cylinders.
+The drill was not successfully grasped showing an example of the case where this method is not applicable.
 The list of these objects as well as their success can be viewed in Fig.
@@
 Of the 20 objects manipulated, 17 were manipulated with no issues, 1 slipped in the grip, and 2 were dropped outright.
+REWRITTEN
 
+\paragraph{}
 \section{Discussion}
@@
 
-Of the objects selected and tested, 15 could be considered pure cylinders.
-Of these cylinders, the only one not successfully manipulated at all was the large flashlight.
-This object slid out of the robot's grasp as it was manipulated.
-A qualitative evaluation of the grasp suggested the fingers were in an appropriate position.
-The flashlight was the heaviest object manipulated by the robot (1 kg) and the friction that the robot could apply through the normal force and the glove material was inadequate to manipulate it.
-The authors believe this is not achievable by the robot regardless of the method of grasp determination.
-In addition, the robot did not maintain a firm grasp on the hammer.
-The hammer shank diameter is at the small end of the range that the robot is able to grasp even with a full hand close position due the kinematics of the hand joints and the friction of the glove.
-The hammer slid in the grasp, but was not dropped.
-In practice, R2 would be able to manipulate this object to a new location.
-R2 maintained solid control of the object for all the other cylinders.
+\subsection{SynGrasp Model Validation}
 
-Four prismatic objects were tested to understand the model applicability outside of a pure cylinder.
-The robot succeeded in manipulating each of these four objects.
-This suggests that this grasp abstracts to more than cylinders, instead, it could be considered a power grasp synergy based on the Cutkosky Grasps, further generalizing the theory.
-
-Finally, the tested synergy was unable to grasp the Dewalt impact driver.
-As the robot closed its hand, the index finger caught on the trigger, not allowing the hand to fully wrap around the handle.
-Upon the rotation action, the Dewalt was dropped.
-This shows that while the synergy concept is useful, it is not directly applicable to all cases and gives an indication of the usefulness of individually actuated joints.
-
-Through the testing, the synergy model proposed successfully manipulated all of the cylindrical objects presented in the experiment, demonstrating the usefulness of the concept in practice.
-The testing also highlighted the further abstraction of the grasp for a cylinder synergy to a power grasp synergy through the manipulation of the prismatic objects.
-Finally, it was demonstrated that while this synergy is useful for cylinders, additional hand DoFs are still necessary for complex manipulations like that of a drill.
-
-%\subsection{SynGrasp Model Validation}
-
-The SynGrasp model provided a very useful method to determine a starting point for grasp refinement.
-The SynGrasp model remains an idealized model of the robot hand.
-Many aspects could not be accurately modeled and had to be adjusted through the model validation process, as discussed below.
+Before the final testing and validation of the system, but SynGrasp model had to be validated.
+The SynGrasp model provided a very useful method to determine a starting point for grasp refinement, however, the SynGrasp model remains an idealized model of the robot hand.
+Many aspects could not be accurately modelled and had to be adjusted through the model validation process, as discussed below.
 Future additions to the software to allow more realistic actuation could include friction models and more control over the geometry of the hand, as R2's palm is larger than the model allowed.
@@
 
-In addition, the 4 DoF thumb has many possible locations in which it could contact the cylinder in SynGrasp, and due to the redundant DoF, the thumb location choice performed poorly for larger objects near 7.62 cm diameter.
+In addition, due to a redundant DoF, the 4 DoF thumb has many possible locations in which it could contact the cylinder in SynGrasp which caused the thumb location choice to perform poorly for larger objects near 7.62 cm diameter.
 Primarily, the thumb would roll too close to the palm, giving a point contact on the thumb pad for larger diameters rather than a wrap around the cylinder.
 The thumb position was adjusted via testing.
-The index and middle finger values still proved valid.
+The index and middle finger generated by SynGrasp were able to be used with no modifications, demonstrating the usefulness of the initial model in testing and validation.
 
@@
 This is a concept the authors are leaving for future work.
+
+\subsection{Grasp Success Discussion}
+Once the model was validated, the final testing of the method could be performed.
+Of the objects selected and tested, 15 could be considered pure cylinders.
+Of these cylinders, the only one not successfully manipulated at all was the large flashlight.
+This object slid out of the robot's grasp as it was manipulated.
+A qualitative evaluation of the grasp suggested the fingers were in an appropriate position.
+The flashlight was the heaviest object manipulated by the robot (1 kg) and the friction that the robot could apply through the normal force and the glove material was inadequate to manipulate it.
+The authors believe this is not achievable by the robot regardless of the method of grasp determination.
+In addition, the robot did not maintain a firm grasp on the hammer.
+The hammer shank diameter is at the small end of the range that the robot is able to grasp even with a full hand close position due the kinematics of the hand joints and the friction of the glove.
+The hammer slid in the grasp, but was not dropped.
+In practice, R2 would be able to manipulate this object to a new location.
+R2 maintained solid control of the object for all the other cylinders.
+
+Four prismatic objects were tested to understand the model applicability outside of a pure cylinder.
+The robot succeeded in manipulating each of these four objects.
+This suggests that this grasp abstracts to more than cylinders, instead, it could be considered a power grasp synergy, further generalizing the theory.
+
+Finally, the tested synergy was unable to grasp the Dewalt impact driver.
+As the robot closed its hand, the index finger caught on the trigger, not allowing the hand to fully wrap around the handle.
+Upon the rotation action, the Dewalt was dropped.
+This shows that while the synergy concept is useful, it is not directly applicable to all cases and gives an indication of the usefulness of individually actuated joints.
+
+Through the testing, the synergy model proposed successfully manipulated all of the cylindrical objects presented in the experiment, demonstrating the usefulness of the concept in practice.
+The testing also highlighted the further abstraction of the grasp for a cylinder synergy to a power grasp synergy through the manipulation of the prismatic objects.
+Finally, it was demonstrated that while this synergy is useful for cylinders, additional hand DoFs are still necessary for complex manipulations like that of a drill.
 
@@
 
-%\subsection{Applicability and Future Work}
-
-%The approach demonstrated in this work shows a useful method of grasping objects commonly manipulated through a power grasp.
+\subsection{Applicability and Future Work}
+RE-ADDED
+The approach demonstrated in this work shows a useful method of grasping objects commonly manipulated through a power grasp.
 There is a simple logical step to then apply these methods to determine the synergies for other types of grasp such as a pinch grasp or ball grasp, and effectively change the Cutkosky grasps from single shapes, to sets of relationships.
@@
 These simple additions could allow individual finger actions that are still intuitive to program to be added to the overall hand motions that have been demonstrated to work.
+RE-ADDED
 

### 2017-10-17 draft_springer_2.tex
editted abstract and the body of the paper for general mistakes

@@
 Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming robots to grasp common objects.
-There exists a need for an efficient method to command high degree-of-freedom (DoF) dexterous manipulators for a range of objects such that explicit models are not needed for every interaction.
-The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoFs to match intuitive measurements of an object, which we term geometrical synergies.
+There exists a need for an efficient method to command high degree-of-freedom (DoF) , position-controlled, dexterous manipulators for a range of objects such that explicit models are not needed for every interaction.
+The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoFs to match intuitive measurements of an object to be grasped, which we term geometrical synergies.
 The approach of this paper is similar to that of Ciocarlie et al.
-\cite{ciocarlieallen}, however, rather than testing the postural synergies that come from the principle components of a human grasps, the authors design a grasping synergy based on the object that is meant to be grasped.
-For this paper, the synergy was designed to grasp cylinder-shaped objects.
+\cite{ciocarlieallen}, however, rather than testing the postural synergies that come from the principle components of a human grasps, the authors design a grasping synergy based on the object that is meant to be grasped by the robot.
+For this paper, a synergy was designed to grasp cylinder-shaped objects.
 Using the SynGrasp toolbox, a model of Robonaut 2`s twelve-DoF hand was created to perform contact analysis around a small set of cylinders defined by a single variable, diameter.
@@
 Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated in a proof-of-concept experiment.
-This synergy-based grasp planning method can be applied to any humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs, to grasp commonly shaped objects, vastly multiplying the library of objects the robot can manipulate.
+This synergy-based grasp planning method can be applied to any position-controlled humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs.
+to grasp commonly shaped objects.
+This method has the potential to vastly multiply the library of objects the robot can manipulate.
 \keywords{Manipulation, Grasp, Synergy, Humanoid, Dexterous Hand}
@@
 This series of 24 position defined grasps composed the main method of grasping an object.
-For full manipulation, the CutKosky grasps are used in conjunction with the Affordance Template Framework \cite{affordance_templates}.
+For full manipulation, the Cutkosky grasps are used in conjunction with the Affordance Template Framework \cite{affordance_templates}.
 This implementation is similar to systems used on other humanoid robots \cite{DRC_Yanco}, \cite{IHMC}.
-However, each of these templates is unique to the object using one of the Cutcosky grasps.
+However, each of these templates is unique to the object using one of the Cutkosky grasps.
 An example Affordance Template is shown in Fig \ref{at_example}.
@@
 
-This creation of templates and gasp positions can be time consuming and very application specific and is intractable at a large scale for robots in practice.
+This creation of templates and grasp positions can be time consuming and very application specific and is intractable at a large scale for robots in practice.
 In addition, the current proposed methods of using the synergies based on the PCA of the human hand are equally non-intuitive to program in a position based scheme.
@@
 The finger position can be commanded based on the single DoF dictated by the diameter of the object.
-This would allow a flash light, a coffee cup, a screwdriver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter.
+This would allow a objects such as a flash light, a coffee cup, a screwdriver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter.
 END REWRITTEN SECTION
@@
 The objective of this study is to build the commanding infrastructure for R2 to take the inputs of synergy type (e.g.
-``cylinder”) and a single variable (e.g.
+cylinder) and a single variable (e.g.
 diameter) and calculate the synergy matrix from these two inputs.
@@
 
-Before the final testing and validation of the system, but SynGrasp model had to be validated.
+Before the final testing and validation of the system, the SynGrasp model needed to be updated and validated.
 The SynGrasp model provided a very useful method to determine a starting point for grasp refinement, however, the SynGrasp model remains an idealized model of the robot hand.

### 2017-10-29 draft_springer_2.tex
updated section 2.2

@@
 To this end, Robonaut 2 is a humanoid robot with two 7 DoF arms (including the wrist), a 3 DoF neck, 1 DoF waist, two 12 DoF hands, and two 7 DoF legs.
-R2 is currently on board the International Space Station.
+R2 is currently on board the International Space Station (see Fig \ref{at_r2_iss}.
 The design goal of this robot is to assist astronauts with repetitive tasks on the International Space Station like monitoring airflow, cleaning handrails, and unpacking resupply vehicles \cite{r2_diftler}.
@@
 To achieve this level of autonomy and dexterity, it becomes intractible to set specific values for each robot joint to form every possible hand pose that R2 might require on board the ISS.
-Currently, each object to be manipulated must be modeled, the approach trajectories made and tested, and the necessary hand positions made and verified.
-However, if the commands to control grasps can be decreased from 12 DoF to 1 DoF, this task becomes significantly simpler.
-Instead of each individual object, a single cylindrical model could be made and verified.
-Then, the robot will have a model to manipulate any cylindrical object encountered.
+Currently, each object to be manipulated must be modeled, the approach trajectories defined and tested, and the necessary hand positions specified and verified.
+However, if the complexity of commands to control grasps can be decreased from 12 DoF to 1 DoF, this task becomes significantly simpler.
+Instead of modeling and planning grasps for each individual object, a single shape-based model could be developed and verified.
+Then, the robot will have a model to manipulate any similarly shaped object encountered.
 The application of synergies in this case will save time and effort while increasing the capability and usefulness of the dexterous robot.

### 2017-10-29 draft_springer_2.tex
updated section 2.3, was current hand pose section.

@@
 
-\subsection{Current R2 Grasping Process}
-REWRITTEN SECTION 
-R2's command structure centers around the concept of multi-loop control with a progressive series of loops \cite{r2_control}.
-The lowest level of control is a current loop, wrapped by a velocity loop, wrapped by a torque loop, and finally wrapped by a position loop that the user is dictating.
-However, the R2 finger actuators are not series elastic and have no direct torque measurement.
-Therefore, the torque loop is removed in the multi-loop control model and current limiting is placed at the lowest level to protect the finger tendons.
-This loop structure eliminates the capability to do direct torque control of the fingers to close around an object, thus dictating the need for a position control scheme to command the hand to manipulate objects.
+\subsection{Current Implementation of R2 Pose and Object Feature Based Grasping}
+R2's command structure centers around the concept of multi-loop control with a series of embedded loops \cite{r2_control}.
+The lowest level of control is a current loop, wrapped by a velocity loop, wrapped by a torque loop, and finally wrapped by a position loop that specified the desired finger poses.
+Because the actuators that position R2's fingers are not series-elastic and have no direct torque measurement capability, the control structure of the R2 hand is modified compared to that used for the series elastic joints in the arms and legs.
+The torque control loop is removed and current limiting is added to the lowest control loop to protect the finger tendons.
+Without hte capability of direct torque control of the finger joints, the fingers can only be position controlled.
+For R2 to grasp complex-shaped objects, precise models of object geometry and accurate position control are required.
+Thus, the postural-syngery based grasp control schemes that have seen success in control of compliant robot hands \cite{} will be ineffective for control of R2.
 
-   \begin{figure}[t]
+   \begin{figure}[!b]
       \centering
@@
 
-Due to this position control scheme, the original grasp process used by R2 was based on the Cutkosky Grasp Taxonomy \cite{Cutkosky}.
+Given the necessity to accurately command finger-joint positions in the R2 hand to achieve grasping, the original grasp process used by R2 was based on the Cutkosky Grasp Taxonomy \cite{Cutkosky}.
 This series of 24 position defined grasps composed the main method of grasping an object.
-For full manipulation, the Cutkosky grasps are used in conjunction with the Affordance Template Framework \cite{affordance_templates}.
-This implementation is similar to systems used on other humanoid robots \cite{DRC_Yanco}, \cite{IHMC}.
-However, each of these templates is unique to the object using one of the Cutkosky grasps.
-An example Affordance Template is shown in Fig \ref{at_example}.
-If a new grasp is needed, it must be created, tested and verified.
-If a new object that is slightly different than a current known object is encountered, a new Affordance Template and grasp must be created and tested.
+For full manipulation, the Cutkosky grasps are used in conjunction with the Affordance Template Framework \cite{affordance_templates} that builds manipulation models for objects to be grasped, similar to systems used for other humanoid robots \cite{DRC_Yanco}, \cite{IHMC}.
+This approach results in unique pairings of a single object affordance template with an appropriate Cutkosky grasp.
+An example affordance template is shown in Fig \ref{at_example}.
+To grasp the object differently, a new grasp must be created, tested, and verified.
+To grasp a new object, even if it differs only slightly from the orignial, the entire affordance template creation process must be repeated.
 
-This creation of templates and grasp positions can be time consuming and very application specific and is intractable at a large scale for robots in practice.
-In addition, the current proposed methods of using the synergies based on the PCA of the human hand are equally non-intuitive to program in a position based scheme.
-Therefore, a commanding structure to determine hand position based on simple properties of the object is proposed.
-Specifically for this work, the authors propose a geometric synergy based on cylindrical type objects.
-The finger position can be commanded based on the single DoF dictated by the diameter of the object.
+This repeated creation of templates and grasp positions can be time consuming and application specific, and is intractable at a large scale for robots in practice.
+Further, the method of using pose-based synergies of the human hand are equally non-intuitive to implement in a position control based scheme.
+A new approach is needed, one that allows for determination of robot hand positions based on simple geometric poerperties of the object to be grasped.
+In this paper, the authors propose a geometric synergy based on cylindrical type objects.
+The finger position can be commanded based on a single variable dictated by the object, it's diameter.
 This would allow a objects such as a flash light, a coffee cup, a screwdriver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter.
-END REWRITTEN SECTION
+
 \section{Methods}

### 2017-10-29 draft_springer_2.tex
updated results section

@@
   \caption{Results from cylindrical synergy testing using the developed curve fits.
-The blue field contrains the pure cylindrical objects.
-The orange contains rectangular prisms, and the yellow contains the only complex geometry object, the drill}
+The blue field contains cylindrical objects.
+The orange contains rectangular prisms, and the yellow contains the complex geometry object, the drill}
   \label{objects} 
@@
 
-REWRITTEN
-After model validation on the robot and subsequent adjustments, the robot was able to manipulate 13 of 15 cylindrical objects in the experiment using the single synergy commanding structure.
-In addition, five non-cylindrical objects were tested, four of which were nearly square rectangular prisms, and one drill.
-All four rectangular prism objects were successfully grasped which demonstrated the applicability of this synergy to more than pure cylinders.
-The drill was not successfully grasped showing an example of the case where this method is not applicable.
-The list of these objects as well as their success can be viewed in Fig.
-\ref{objects}.
+The robot was able to successfully manipulate 13 of 15 cylindrical objects in the experiment using the geometric synergy commanding structure based on object diameter.
+All four rectangular prism objects were successfully grasped which demonstrated the robustness of the geometric synergy control scheme based on cylinders.
 Of the 20 objects manipulated, 17 were manipulated with no issues, 1 slipped in the grip, and 2 were dropped outright.
-REWRITTEN
+A summary of the results is presented in Fig \ref{objects}.
 
@@
 
-Before the final testing and validation of the system, the SynGrasp model needed to be updated and validated.
-The SynGrasp model provided a very useful method to determine a starting point for grasp refinement, however, the SynGrasp model remains an idealized model of the robot hand.
+The SynGrasp model provided a useful method to determine a starting point for grasp refinement, however, the SynGrasp model remains an idealized model of the robot hand.
 Many aspects could not be accurately modelled and had to be adjusted through the model validation process, as discussed below.

### 2017-10-29 draft_springer_2.tex
Section 5.1 updated

@@
 Future additions to the software to allow more realistic actuation could include friction models and more control over the geometry of the hand, as R2's palm is larger than the model allowed.
-Going forward, SynGrasp is useful for other synergy types such as pinch grasp which has contact forces only in the fingers and does not require use of the palm.
 
@@
 On the R2 hand, especially on the ring and little fingers, the first joint will move exclusively until it comes into contact with the object, then the next joints will begin to actuate.
-This resulted in poor finger placement for the ring and little fingers on initial model validation and the closing values had to be increased to obtain a firm grip using those fingers.
-The result of this can be seen in Fig.
-\ref{pinkymodels}
+This resulted in poor finger placement for the ring and little fingers on initial model validation and the closing values had to be increased to obtain a firm grip using those fingers (see Fig \ref{pinkymodels}).
 

### 2017-10-29 draft_springer_2.tex
updated 5.2, removed 5.3, updated conclusions.

@@
   \caption{Initial (a) and final (b) joint angles for ring and little fingers.
-The initial round of testing following SynGrasp model generation resulted in no contact in the ring and little fingers.
-This result in due to tendon friction in the actual system that reduced the closure angle to a lower value than commanded.}%
+The initial round of testing following SynGrasp model generation resulted in no contact in the ring and little fingers due to tendon friction in the actual system that reduced the closure angle to a lower value than commanded.}%
 \label{pinkymodels}%
@@
 
-In addition, due to a redundant DoF, the 4 DoF thumb has many possible locations in which it could contact the cylinder in SynGrasp which caused the thumb location choice to perform poorly for larger objects near 7.62 cm diameter.
-Primarily, the thumb would roll too close to the palm, giving a point contact on the thumb pad for larger diameters rather than a wrap around the cylinder.
-The thumb position was adjusted via testing.
-The index and middle finger generated by SynGrasp were able to be used with no modifications, demonstrating the usefulness of the initial model in testing and validation.
+Due to a redundant DoF, the 4 DoF thumb has many possible locations in which it could contact the cylinder in SynGrasp. 
+This resulted in non-ideal thumb location choices near 7.62 cm diameter.
+Primarily, the thumb would roll too close to the palm, giving a point contact on the thumb pad rather than a wrap around the cylinder.
+The thumb position was adjusted during validation of the SynGrasp model on the R2 hand.
+The index and middle finger positions generated by SynGrasp were able to be used with no modifications.
+Overall, the initial joint angles generated by the SynGrasp model resulted in successful grasps of the test objects in a majority of cases, demonstrating the useflness of the methodology.
 
-A result from the grasping tests was that cylinders near 10 cm were grasped by the robot in a pinch grasp fashion due to the size, so a future pinch grasp model could incorporate larger objects.
-Also, the geometric synergy method was unable to handle the complex geometry of the drill, which demonstrates that while the synergy concept is useful, it is not directly applicable to all cases and gives an indication of the usefulness of individually actuated joints.
+A result from the grasping tests was that cylindrical objects with diameters near 10 cm were grasped by the robot in a pinch grasp fashion.
+Future refinements of this geometric-based synergy scheme might explore alternative strategies for larger objects.
+Also, the geometric synergy method was unable to handle the complex geometry of the drill, which demonstrates that while the synergy concept is useful, it is not directly applicable to all.
 Typical manipulation of this tool has the index finger extended, allowing the other fingers to wrap underneath using the synergy-based cylinder grasp values.
@@
 
-\subsection{Grasp Success Discussion}
-Once the model was validated, the final testing of the method could be performed.
-Of the objects selected and tested, 15 could be considered pure cylinders.
-Of these cylinders, the only one not successfully manipulated at all was the large flashlight.
-This object slid out of the robot's grasp as it was manipulated.
-A qualitative evaluation of the grasp suggested the fingers were in an appropriate position.
-The flashlight was the heaviest object manipulated by the robot (1 kg) and the friction that the robot could apply through the normal force and the glove material was inadequate to manipulate it.
-The authors believe this is not achievable by the robot regardless of the method of grasp determination.
-In addition, the robot did not maintain a firm grasp on the hammer.
-The hammer shank diameter is at the small end of the range that the robot is able to grasp even with a full hand close position due the kinematics of the hand joints and the friction of the glove.
-The hammer slid in the grasp, but was not dropped.
-In practice, R2 would be able to manipulate this object to a new location.
-R2 maintained solid control of the object for all the other cylinders.
+\subsection{Grasp Success}
 
-Four prismatic objects were tested to understand the model applicability outside of a pure cylinder.
+The geometric-based synergy model successfully manipulated all of the cylindrical objects presented in the experiment, demonstrating the usefulness of the concept in practice.
+The testing also highlighted the further abstraction of the grasp for a cylinder synergy four prismatic objects that could be approximated as cylindersto.
+Finally, it was demonstrated that while this synergy is useful for cylinders, other methods are still necessary for complex manipulations like that of a drill.
+
+Of the 15 cylindrical objects manipulated by the robot, two failures occured.
+In one case, the diameter of the object (hammer) was at he low end of the range tested.
+Even with a complete closure grasp, the hammer slid in the grasp, but was not dropped.
+Friction between R2's glove material and the object combined with the kinematic limitations of the finger joints appeared to be the cause of the failure, rather than the geometric-based synergy model.
+In the second failure, the robot was unable to manipulate the large flashlight without dropping it.
+While the fingers were positioned in an appropriate orientation relative to the object, the weight of the object (~1kg, heaviest of the set tested) and friction between between the glove and object appeared to be the root cause of the failure.
+In practice, the Cutkosky grasp plus affordance template method of grasp designed for the hammer and flashlight for the specific object geometry resulted in the same failures.
+
+Four prismatic objects were tested to understand the model applicability for shapes other than a pure cylinder.
 The robot succeeded in manipulating each of these four objects.
-This suggests that this grasp abstracts to more than cylinders, instead, it could be considered a power grasp synergy, further generalizing the theory.
+This suggests that this grasp abstracts to more than cylinders, instead, the geometric-based synergy is effective for ojects that could be closely approximated as cylinders.
 
-Finally, the tested synergy was unable to grasp the Dewalt impact driver.
+Finally, the robot was unable to grasp the complex shape of the Dewalt impact driver.
 As the robot closed its hand, the index finger caught on the trigger, not allowing the hand to fully wrap around the handle.
-Upon the rotation action, the Dewalt was dropped.
-This shows that while the synergy concept is useful, it is not directly applicable to all cases and gives an indication of the usefulness of individually actuated joints.
-
-Through the testing, the synergy model proposed successfully manipulated all of the cylindrical objects presented in the experiment, demonstrating the usefulness of the concept in practice.
-The testing also highlighted the further abstraction of the grasp for a cylinder synergy to a power grasp synergy through the manipulation of the prismatic objects.
-Finally, it was demonstrated that while this synergy is useful for cylinders, additional hand DoFs are still necessary for complex manipulations like that of a drill.
+During the rotation action, the object was dropped.
+While the geometric-based synergy approach to grasping is applicable to shapes beyond those used in design and validation, the approach has limiations.
+In cases of complex geometry, other methods may be preferred.
 
@@
 
-\subsection{Applicability and Future Work}
-RE-ADDED
-The approach demonstrated in this work shows a useful method of grasping objects commonly manipulated through a power grasp.
-There is a simple logical step to then apply these methods to determine the synergies for other types of grasp such as a pinch grasp or ball grasp, and effectively change the Cutkosky grasps from single shapes, to sets of relationships.
+%\subsection{Applicability and Future Work}
+
+%The approach demonstrated in this work shows a useful method of grasping simple objects commonly manipulated through a cylindrical grasp.
+There is a simple logical step to then apply these methods to determine the geometric-based synergies for other types of grasp such as a pinch grasp or ball grasp, and effectively change the Cutkosky grasps from single shapes, to sets of relationships.
 However, to truly do human type manipulation, the individually commanded DoF must remain as shown with the Dewalt drill manipulation.
@@
 These simple additions could allow individual finger actions that are still intuitive to program to be added to the overall hand motions that have been demonstrated to work.
-RE-ADDED
 
@@
 
-The authors demonstrated a novel concept to incorporate the synergy framework developed in neuroscience and analyzed in practice  into an intuitive commanding strategy for a high DoF robot hand on Robonaut 2.
-The creation of a synergy based on the diameter of a cylindrical object allowed cylinders of varying sizes to be effectively grasped via a single command input.
-The results of this test suggest that this concept could be used to quickly broaden the library of objects the robot can manipulate from a small, specialized set, into a nearly infinite library of manipulatable cylinders.
+The authors demonstrated a novel concept to modify the postural synergy framework developed in neuroscience into an intuitive commanding strategy for high DoF, position controlled robot hands that parameterizes the object to be grasped.
+The creation of a geometric synergy based on the diameter of a cylindrical object allowed cylinders of varying sizes to be effectively grasped via a single command input.
+The results of this test suggest that this concept could be used to quickly broaden the library of objects the robot can manipulate from a small, specialized set, into a nearly infinite library of manipulatable cylinders and other common shapes.
 

### 2017-10-29 draft_springer_2.tex
update abstract,intro, methods

@@
 Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming robots to grasp common objects.
-There exists a need for an efficient method to command high degree-of-freedom (DoF) , position-controlled, dexterous manipulators for a range of objects such that explicit models are not needed for every interaction.
+There exists a need for an efficient method to command high degree-of-freedom (DoF) , position-controlled, dexterous manipulators to grasp a range of objects such that explicit models are not needed for every interaction.
 The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoFs to match intuitive measurements of an object to be grasped, which we term geometrical synergies.
-The approach of this paper is similar to that of Ciocarlie et al.
-\cite{ciocarlieallen}, however, rather than testing the postural synergies that come from the principle components of a human grasps, the authors design a grasping synergy based on the object that is meant to be grasped by the robot.
+Rather than testing the postural synergies that come from the principle components of human grasps, the authors design a grasping synergy based on the object that is meant to be grasped by the robot.
 For this paper, a synergy was designed to grasp cylinder-shaped objects.
-Using the SynGrasp toolbox, a model of Robonaut 2`s twelve-DoF hand was created to perform contact analysis around a small set of cylinders defined by a single variable, diameter.
-Experiments were performed on the robot to validate and update the synergy-based models.
+Using the SynGrasp toolbox, a model of a twelve-DoF hand was created to perform contact analysis around a small set of cylinders defined by a single variable, diameter.
+Experiments were performed with the robot to validate and update the synergy-based models.
 Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated in a proof-of-concept experiment.
-This synergy-based grasp planning method can be applied to any position-controlled humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs.
-to grasp commonly shaped objects.
+This geometric synergy-based grasp planning method can be applied to any position-controlled humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs in order to grasp commonly shaped objects.
 This method has the potential to vastly multiply the library of objects the robot can manipulate.
@@
 Humanoid robots provide the capability to operate in the same space, using the same tools that a human can.
-The future of these robots can clearly be seen with efforts for robots to go into disaster areas unsafe for humans \cite{fukushima_robots} or help humans do menial tasks.
+The future of these robots can clearly be seen with efforts for robots to go into disaster areas unsafe for humans \cite{fukushima_robots} or help humans complete menial tasks.
 Perhaps the most fundamental capability necessary to accomplish these human tasks is the ability to manipulate the same objects that humans can.
-For this challenge, many designers have created hands capable of nearly all of the DoFs as the human hand \cite{r2_hand}, \cite{DRL}, \cite{hrp3}, \cite{softhand}.
+For this challenge, designers have created hands capable of nearly all of the DoFs as the human hand \cite{r2_hand}, \cite{DRL}, \cite{hrp3}, \cite{softhand}.
 However, while the hands are able to form many of the same grips and poses as a human hand, the control of these hands in an intuitive and simple way has yet to be demonstrated.
@@
 These groups combine to create the plethora of hand motions humans can form \cite{Santello} \cite{neuro}.
-This approach gives a method for decreasing the commanded DoF of the hand system to a more manageable number, and is referred to as ``synergies".
-These synergy schemes represent the principle components of various grasps of the human hand.
-These components can be difficult to intuitively combine into useful hand motions, shifting the complexity problem from DoF, to nonintuitive combinations of synergies.
+This approach gives a method for decreasing the commanded DoF of the hand system to a more manageable number, and is referred to as synergy-based control.
+These synergy schemes represent the principal components of various grasps of the human hand.
+These principal components can be difficult to intuitively combine into useful hand motions, shifting the complexity problem from DoF, to nonintuitive combinations of synergies.
+In contrast, we propose a method of reducing the command complexity by developing geometrical synergies that capture the shape characteristics of the object to be grasped.
 \par
-The contribution of this paper is a methodology to decrease the commanded DoF from twelve to one for the Robonaut 2 (R2) hand to manipulate simple cylindrical shapes.
-This methodology replaces all unique cylindrical type models with a single model to allow simple manipulation of common objects.
+The specific contribution of this paper is a methodology to decrease the commanded DoF from twelve to one for the Robonaut 2 (R2) humanoid robot hand to manipulate simple cylindrical shapes.
+Our methodology replaces all unique cylindrical type models with a single model to allow simple manipulation of common objects.
 In addition, the single commanded DoF is based on a simple measurement of the object to allow intuitive control.
@@
 These devices are high DoF systems that allow robots to manipulate objects in similar ways to a human.
-However, as this problem has been studied further, the construction of robotic hands with similar DoFs as the human hand has become common place, but the control is anything but intuitive.
+While the construction of robotic hands with similar DoFs as the human hand has become common place, the control of these complex devices is anything but intuitive.
 The computational costs to calculate the correct closing position around a given object as perceived by a robotic vision system is $O(2^N)$
@@
 Santello et al.
-performed Principal Component Analysis (PCA) on a large range of everyday grasps, and was able to model 50$\%$ of the variability in the grasps with a single relationship, or synergy.
+performed Principal Component Analysis (PCA) on a large range of everyday grasps, and were able to model 50$\%$ of the variability in the grasps with a single relationship, or synergy.
 If a second synergy was added in proportion, roughly 80$\%$  of the variability in grasps could be commanded.
 Similarly the third synergy resulted in modeling 90$\%$  of observed grasp variability.
-This coupling demonstrates how our brain is potentially reducing the 20 DoF problem of hand motion into only a few DoFs.
+This coupling demonstrates how our brain is potentially reducing the 20 DoF problem of hand pose control into only a few DoFs.
 Thinking in this way greatly reduces the complexity of grasping for humans and allows smooth control of a very large number of DoFs to accomplish grasping  tasks without a large burden on the nervous system.
 
- Engineers can draw inspiration from this structure to design robotic grasping devices.
+ Engineers can draw inspiration from this structure to design robotic grasping methods.
 A synergistic scheme can be implemented in several ways.
@@
 They can also be used to devise under-actuation schemes such as the PISA-IIT soft-hand \cite{softhand}.
-Finally, they can be used to simplify the control of fully actuated hands by creating ``Software Synergies" \cite{catalano_2012_adaptive}.
+Finally, they can be used to simplify the control of fully actuated hands by creating \textit{Software Synergies} \cite{catalano_2012_adaptive}.
 
@@
 \cite{power_grasp} used a more involved algorithm to study the contacts on complex objects by partitioning the object into planar slices, studying form and force closure  \cite{bicchi} to determine optimal hand closure.
-An interesting aspect of this approach was it calculated the optimal thumb and index finger closure, and then calculated the remaining fingers to stabilize the grasp.
+An interesting aspect of this approach was that it calculated the optimal thumb and index finger closure, and then calculated the remaining fingers to stabilize the grasp.
 Garcia et.
@@
 
-SynGrasp, a MATLAB toolbox developed for the purpose of simulating underactuated robot grasping, is another computational tool based on synergies \cite{syngrasp}.
-This toolbox offers three primary capabilities: it allows the user to model robotic hands, perform grasp simulations and analysis, and map synergies on to robot hand designs.
+SynGrasp, a MATLAB toolbox developed for the purpose of simulating underactuated robot grasping, is another computational tool based on postural synergies \cite{syngrasp}.
+This toolbox offers three primary capabilities: it allows the user to model robotic hands, perform grasp simulations and analysis, and map synergies onto robot hand designs.
 SynGrasp is well suited to designing and testing  synergy schemes using kinematics \cite{salvietti_2016_map}.
-We also aim to create our own unique purpose-driven synergy scheme instead of attempting to replicate human postural synergies.
+In this work, we aim to create our own unique purpose-driven synergy scheme, rather than attempting to replicate human postural synergies.
 
-The ability to create user-defined hand models and synergies makes SynGrasp an ideal tool for simulating a synergy based command structure on R2.
-A computational tool for modeling grasps and commands would be hugely beneficial for evaluation of the hand and for designing grips for it.
+The ability to create user-defined hand models and synergies makes SynGrasp an ideal tool for simulating a synergy based command structure on Robonaut 2 (R2).
+A computational tool for modeling grasps and commands would be hugely beneficial for evaluation of the hand and for grasp design.
 %replace this sentence
-While the main purpose of this study is to evaluate a synergy command architecture, it will have the added objective of evaluating the use and accuracy of SynGrasp simulations in real-world environments.
+While the main purpose of this study is to evaluate a geometry-based synergy command architecture, it has the added objective of evaluating the use and accuracy of SynGrasp simulations in real-world environments.
 
@@
 To this end, Robonaut 2 is a humanoid robot with two 7 DoF arms (including the wrist), a 3 DoF neck, 1 DoF waist, two 12 DoF hands, and two 7 DoF legs.
-R2 is currently on board the International Space Station (see Fig \ref{at_r2_iss}.
+R2 is currently on board the International Space Station (see Fig \ref{at_r2_iss}).
 The design goal of this robot is to assist astronauts with repetitive tasks on the International Space Station like monitoring airflow, cleaning handrails, and unpacking resupply vehicles \cite{r2_diftler}.
@@
 To achieve this level of autonomy and dexterity, it becomes intractible to set specific values for each robot joint to form every possible hand pose that R2 might require on board the ISS.
-Currently, each object to be manipulated must be modeled, the approach trajectories defined and tested, and the necessary hand positions specified and verified.
+Currently, each object to be manipulated must be modeled, the approach trajectories defined and tested, and the necessary hand positions constructed and verified.
 However, if the complexity of commands to control grasps can be decreased from 12 DoF to 1 DoF, this task becomes significantly simpler.
@@
 $S$ is a vector of weights that determines the amount of motion for an individual joint resulting from a single input.
-In neuroscience, these $S$ matrices are determined by mapping the grasps of various shapes and isolating the movements of individual joints.
+When using a pose-based synergy scheme, these $S$ matrices are determined by observing a subject grasp and manipulate various objects and isolating the movements of individual joints.
 The covariances of the various joint angles are analyzed and combined using machine learning to identify when joints are commonly moved in unison, a weighting scalar based on the relative magnitude of motion.
-Rather than identifying and isolating synergies from existing behaviour as is done in neuroscience, the authors aim to design a synergy by providing an $S$ matrix such that the finger joints move in unison to produce a cylinder grasp.
-For this reason, the synergy matrix is designed based on grasp shapes for various sized cylinders.
 
-The objective of this study is to build the commanding infrastructure for R2 to take the inputs of synergy type (e.g.
+In contrast, the authors aim to design a geometry-based synergy control scheme by providing an $S$ matrix such that the finger joints move in unison to produce a cylinder grasp.
+To acheive this geometry-based synergy control scheme, we describe our process for building the commanding infrastructure for R2 to take the inputs of synergy type (e.g.
 cylinder) and a single variable (e.g.
 diameter) and calculate the synergy matrix from these two inputs.
-The q matrix of joint angles will need to then be passed to the robot to command the fingers joints to the calculated angles.
+The \textit{q} matrix of joint angles will then be passed to the robot to move the fingers joints to the calculated angles.
 
@@
 
-The first step is to determine the finger angles for grasps of cylinders of varying diameter using SynGrasp to build an initial model for grasping.
-The chosen diameters for grasped objects were 2.54 cm, 3.81 cm, 5.08 cm, and 7.62 cm.
+The first step is to build an initial model for grasping by determining the finger angles for grasps of cylinders of specific diameters that span the size range of objects that might be encountered in the workspace.
+For our application, the chosen diameters for grasped objects were 2.54 cm, 3.81 cm, 5.08 cm, and 7.62 cm.
+For the program, the objects were considered massless.
 The internal contact model in SynGrasp was used to design the grip.
-This performed better than traditional inverse kinematic models because it allowed contact with multiple points on the hand rather than only a single point-of-interest on the end-effector.
-The key features such as the number of DoFs, finger length, joint rotation frames, and actuation scheme were matched.
-Some areas where the modeling program could not match the actual R2 hand were the compliance of the fingers and the size of the palm.
+This model performed better than traditional inverse kinematic models because it allowed contact with multiple points on the hand rather than only a single point-of-interest on the end-effector.
+The key features of the R2 hand such as the number of DoFs, finger length, joint rotation frames, and actuation scheme were matched.
+The SyGrasp toolbox did not allow for representation of the R2 hands physical compliance, nor could the geometry of the palm be accurately represented.
+
+The SynGrasp model was then provided a synergy matrix that reflected the R2 hand control scheme and its constraings.
 The Robonaut hand contains 18 movable DoFs but only 12 controllable DoFs.
@@
 These two fingers have no yawing DoF at the MCP.
-The SynGrasp model was provided a synergy matrix to reflect this scheme and grips were designed to include these constraints.
 
@@
 
-\subsection{Testing Method} 
-A simple testing method was used to validate the models, as well as perform the final experiments to determine grasp efficacy.
+\subsection{Model Refinement and Synergy Development} 
+A simple testing method was used to validate the initial SynGrasp models.
 A cylindrical object was placed on the table, touching R2's open palm.
@@
 Then, the robot was commanded to close its hand based on the synergy values, lift the object, rotate the object upside down, return it to straight, and finally, release it back on the table.
-This set of motions demonstrates a firm grasp on the object through a large motion of the robot.
+Successful completion of this set of motions demonstrates a firm grasp on the object through a large motion of the robot.
 
@@
 
-\subsection{Model Refinement and Synergy Development}
-The models were validated by commanding R2's hand to close around a cylindrical piece of aluminum exactly equal to our modeled diameter using the values dictated by SynGrasp.
-The grasps were tested and refined using the previously mentioned test method and the model discrepancies were accounted for.
-These discrepancies are discussed in detail in Section \ref{discussion}.
-Once the final values from testing were established, the results from each cylinder diameter for each finger were plotted and a polynomial fit to the data was carried out.
+Four cylindrical validation objects were used in the initial testing, each having a diameter equal to the values provided to the SynGrasp toolbox during the modeling phase.
+Since the SynGrasp model was not a perfect replication of the R2 hand, small adjustments to the grasp model were required to correct finger and thumb placement (for a detailed discussion, see section \ref{discussion}) Once the final joint angle values were established, the joint angles for each cylindrical validation object and each R2 finger were plotted and a polynomial fit to the data was carried out.
 The fits were calculated so that the maximum error for each data point was 4 degrees.
-The maximum order used was three, however, many of the joints required lower orders.
-The resulting relationships were relatively simple which intuitively makes sense, as the object gets larger, the hand opens more.
+The maximum polynomial order used was three.
+The resulting relationships between joint angles and object diameters were relatively simple, which  makes sense; as the object gets larger, the hand opens more.
 The thumb is the only digit which changed orientations substantially as the diameters got larger as it has more DoF to move into a suitable position.
@@
 \ref{thumb_fits}.
+This plot is representative of the plots generated for each digit of the R2 hand.
+
+\subsection{Testing Protocol}
+After adjusting the grasp models and generating the joint angle fits to data for the four cylindrical validation objects, fifteen objects typically picked up with a cylindrical grasp were manipulated using the R2 hand and the SynGrasp geometrical synergy grasping model.
+These objects ranged from 2.79 to 8.4 cm in diameter and 5 g to 1.02 kg in mass.
+In addition, five non-cylindrical objects were manipulated using the same action illustrated in \ref{thumb_fits}.
+These objects included four shapes resembling rectangular prisms and one hand drill.
+For a grasp to be considered successfull, the object needed to be successfully held by R2, lifted from a table top and be held without slipping as it was rotated by the robot as shown in Fig.
+\ref{testing}.
 
@@
   \centering
-  \includegraphics[width=1.08\linewidth]{Thumb_Fits_2}
+  \includegraphics[width=1.08\linewidth]{thumb_fits_3}
   \caption{Thumb joint angles when grasping cylinders of varying diameter.  The curve fit shows interpolation between collected data points.}

### 2017-10-30 draft_springer_2.tex
updated per Julias edits

@@
 \begin{abstract}
-Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming robots to grasp common objects.
-There exists a need for an efficient method to command high degree-of-freedom (DoF) , position-controlled, dexterous manipulators to grasp a range of objects such that explicit models are not needed for every interaction.
-The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoFs to match intuitive measurements of an object to be grasped, which we term geometrical synergies.
-Rather than testing the postural synergies that come from the principle components of human grasps, the authors design a grasping synergy based on the object that is meant to be grasped by the robot.
+Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots outside of a controlled laboratory setting is limited in part due to the complexity involved in programming robots to grasp common objects.
+There exists a need for an efficient method to command high degree-of-freedom (DoF) position-controlled dexterous manipulators to grasp a range of objects such that explicit models are not needed for every interaction.
+The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoF to match intuitive measurements of an object to be grasped, which the authors term geometrical synergies.
+Rather than testing the postural synergies that come from the principal components of human grasps, a grasping synergy based on the object to be grasped was designed.
 For this paper, a synergy was designed to grasp cylinder-shaped objects.
@@
 Experiments were performed with the robot to validate and update the synergy-based models.
-Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated in a proof-of-concept experiment.
+Successful manipulation of a large range of cylindrical objects not previously introduced to the robot was demonstrated.
 This geometric synergy-based grasp planning method can be applied to any position-controlled humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs in order to grasp commonly shaped objects.
-This method has the potential to vastly multiply the library of objects the robot can manipulate.
+This method has the potential to vastly expand the library of objects the robot can manipulate.
 \keywords{Manipulation, Grasp, Synergy, Humanoid, Dexterous Hand}
@@
 
-Humanoid robots provide the capability to operate in the same space, using the same tools that a human can.
-The future of these robots can clearly be seen with efforts for robots to go into disaster areas unsafe for humans \cite{fukushima_robots} or help humans complete menial tasks.
-Perhaps the most fundamental capability necessary to accomplish these human tasks is the ability to manipulate the same objects that humans can.
-For this challenge, designers have created hands capable of nearly all of the DoFs as the human hand \cite{r2_hand}, \cite{DRL}, \cite{hrp3}, \cite{softhand}.
+Humanoid robots provide the capability to operate in the same space as humans and use the same tools that humans do.
+The future of these robots is evident in the efforts for robots to go into disaster areas unsafe for humans \cite{fukushima_robots} or help humans complete menial tasks.
+Perhaps the most fundamental capability necessary to accomplish these human tasks is the ability to manipulate the same objects that humans do.
+For this challenge, designers have created hands capable of nearly all of the DoF as the human hand \cite{r2_hand}, \cite{DRL}, \cite{hrp3}, \cite{softhand}.
 However, while the hands are able to form many of the same grips and poses as a human hand, the control of these hands in an intuitive and simple way has yet to be demonstrated.
@@
 The specific contribution of this paper is a methodology to decrease the commanded DoF from twelve to one for the Robonaut 2 (R2) humanoid robot hand to manipulate simple cylindrical shapes.
-Our methodology replaces all unique cylindrical type models with a single model to allow simple manipulation of common objects.
+The methodology replaces all unique cylindrical type models with a single model to allow simple manipulation of common objects.
 In addition, the single commanded DoF is based on a simple measurement of the object to allow intuitive control.
-This enables the robot to successfully manipulate any cylindrical object found in its environment with the single model.
+This enables the robot to successfully manipulate any cylindrical object found in its environment using a single model.
 
@@
 \subsection{Hand Synergies}
-	Dexterous manipulation in robots has developed from a simple parallel gripper towards the complexity of the human hand in the past decades.
+	Dexterous manipulation in robots has developed from a simple parallel gripper to nearly the complexity of the human hand in the past decades.
 These devices are high DoF systems that allow robots to manipulate objects in similar ways to a human.
-While the construction of robotic hands with similar DoFs as the human hand has become common place, the control of these complex devices is anything but intuitive.
+While the construction of robotic hands with similar DoF as the human hand has become more prevalent, the control of these complex devices is anything but intuitive.
 The computational costs to calculate the correct closing position around a given object as perceived by a robotic vision system is $O(2^N)$
- where N represents the number of DoFs, with each DoF controlled individually.
-Researchers have focused on analyzing the way that humans control our own hands with hopes of extending that same control scheme to a robotic hand, as in the seminal work on postural synergies of human grasping \cite{Santello}.
+ where N represents the number of DoF, with each DoF controlled individually.
+Researchers have focused on analyzing the way that humans control their hands with hopes of extending that same control scheme to a robotic hand, such as in the seminal work on postural synergies of human grasping \cite{Santello}.
 
 Neurological studies have demonstrated that the human brain does not plan and execute specific movements of the individual finger joints.
-Instead, our brain will send high level commands down through the motor cortex to execute sets of actions, and these commands will travel down the spine to activate sets of muscles in combination, rather than just single muscle groups.
+Instead, the human brain will send high level commands down through the motor cortex to execute sets of actions, and these commands will travel down the spine to activate sets of muscles in combination, rather than just single muscle groups.
 In this way, our brain is grouping and combining sets of commands in different ways to accomplish the task \cite{neuro}.
 Santello et al.
-performed Principal Component Analysis (PCA) on a large range of everyday grasps, and were able to model 50$\%$ of the variability in the grasps with a single relationship, or synergy.
+performed a Principal Component Analysis (PCA) on a large range of everyday grasps, and were able to model 50$\%$ of the variability in the grasps with a single relationship, or synergy.
 If a second synergy was added in proportion, roughly 80$\%$ of the variability in grasps could be commanded.
 Similarly the third synergy resulted in modeling 90$\%$ of observed grasp variability.
-This coupling demonstrates how our brain is potentially reducing the 20 DoF problem of hand pose control into only a few DoFs.
-Thinking in this way greatly reduces the complexity of grasping for humans and allows smooth control of a very large number of DoFs to accomplish grasping  tasks without a large burden on the nervous system.
+This coupling demonstrates how the human brain is potentially reducing the 20 DoF problem of hand pose control into only a few  DoF.
+Thinking in this way greatly reduces the complexity of grasping for humans and allows smooth control of a very large number of  DoF to accomplish grasping tasks without a large burden on the nervous system.
 
@@
 A synergistic scheme can be implemented in several ways.
-Human hand synergies can be used to identify key DoFs that are necessary for a simplified hand design.
+Human hand synergies can be used to identify key  DoF that are necessary for a simplified hand design.
 They can also be used to devise under-actuation schemes such as the PISA-IIT soft-hand \cite{softhand}.
@@
 \cite{power_grasp} used a more involved algorithm to study the contacts on complex objects by partitioning the object into planar slices, studying form and force closure \cite{bicchi} to determine optimal hand closure.
-An interesting aspect of this approach was that it calculated the optimal thumb and index finger closure, and then calculated the remaining fingers to stabilize the grasp.
+An interesting aspect of this approach was that it calculated the optimal thumb and index finger closure, and then used the remaining fingers to stabilize the grasp.
 Garcia et.
 al.
-demonstrated how human synergy based motion planning can be used to decrease the computation time for motion planning in humanoid dual arm robot system  \cite{garcia}.
+demonstrated how human synergy-based motion planning can be used to decrease the computation time for motion planning in a humanoid dual arm robot system \cite{garcia}.
 
@@
 SynGrasp is well suited to designing and testing synergy schemes using kinematics \cite{salvietti_2016_map}.
-In this work, we aim to create our own unique purpose-driven synergy scheme, rather than attempting to replicate human postural synergies.
+In this work, the authors aim to create a unique purpose-driven synergy scheme, rather than attempting to replicate human postural synergies.
 
 The ability to create user-defined hand models and synergies makes SynGrasp an ideal tool for simulating a synergy based command structure on Robonaut 2 (R2).
-A computational tool for modeling grasps and commands would be hugely beneficial for evaluation of the hand and for grasp design.
-%replace this sentence
 While the main purpose of this study is to evaluate a geometry-based synergy command architecture, it has the added objective of evaluating the use and accuracy of SynGrasp simulations in real-world environments.
@@
 
-NASA is actively developing humanoid robotics to work in the same environment as astronauts.
+NASA is actively developing humanoid robots to work in the same environment as astronauts.
 To this end, Robonaut 2 is a humanoid robot with two 7 DoF arms (including the wrist), a 3 DoF neck, 1 DoF waist, two 12 DoF hands, and two 7 DoF legs.
-R2 is currently on board the International Space Station (see Fig \ref{at_r2_iss}).
-The design goal of this robot is to assist astronauts with repetitive tasks on the International Space Station like monitoring airflow, cleaning handrails, and unpacking resupply vehicles \cite{r2_diftler}.
+R2 is currently on board the International Space Station (ISS) (see Fig \ref{at_r2_iss}).
+The design goal of this robot is to assist astronauts with care-taking tasks on the ISS like monitoring airflow, cleaning handrails, and unpacking resupply vehicles \cite{r2_diftler}.
 Currently, NASA is actively developing technologies to allow this robot to behave with more autonomy.
@@
 R2's command structure centers around the concept of multi-loop control with a series of embedded loops \cite{r2_control}.
-The lowest level of control is a current loop, wrapped by a velocity loop, wrapped by a torque loop, and finally wrapped by a position loop that specified the desired finger poses.
+The lowest level of control is a current loop, wrapped by a velocity loop, wrapped by a torque loop, and finally wrapped by a position loop that specified the desired joint poses.
 Because the actuators that position R2's fingers are not series-elastic and have no direct torque measurement capability, the control structure of the R2 hand is modified compared to that used for the series elastic joints in the arms and legs.
 The torque control loop is removed and current limiting is added to the lowest control loop to protect the finger tendons.
-Without hte capability of direct torque control of the finger joints, the fingers can only be position controlled.
-For R2 to grasp complex-shaped objects, precise models of object geometry and accurate position control are required.
-Thus, the postural-syngery based grasp control schemes that have seen success in control of compliant robot hands \cite{} will be ineffective for control of R2.
+Without the capability of direct torque control of the finger joints, the fingers cannot actuate using force closure schemes.
+For R2 to grasp complex-shaped objects, models of object geometry and position control are required.
+Thus, the postural-syngery based grasp control schemes that have seen success in control of compliant robot hands \cite{softhand} may be less effective for control of R2.
 
@@
 Further, the method of using pose-based synergies of the human hand are equally non-intuitive to implement in a position control based scheme.
-A new approach is needed, one that allows for determination of robot hand positions based on simple geometric poerperties of the object to be grasped.
+A new approach is needed, one that allows for determination of robot hand positions based on simple geometric properties of the object to be grasped.
 In this paper, the authors propose a geometric synergy based on cylindrical type objects.
-The finger position can be commanded based on a single variable dictated by the object, it's diameter.
-This would allow a objects such as a flash light, a coffee cup, a screwdriver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter.
+The finger position can be commanded based on a single variable dictated by the object, its diameter.
+This would allow objects such as a flash light, a coffee cup, a screwdriver, and any other cylinder to be manipulated using the same cylindrical template based solely on the object's diameter.
 
@@
 % take this section from 3 paragraphs down to 3 sentences. We basically say all of this somewhere else. 
-A synergistic command structure can be mathematically defined in (1).
+A synergistic command structure can be mathematically defined as
 $$
@@
 where $q$ is the vector of joint angles of dimensions [$N \times 1$], $N$ is the number of synergies, $S$ is the synergy matrix of dimensions [$N \times M$], $M$ is the number of possible synergies that can be activated and $\sigma$ is the [$M \times 1$] synergy activation vector which determines which synergy or combination thereof is turned on.
-The basis of synergies is that the generic joint displacement, $q$, can be represented as a function of fewer elements than the number of DoFs of the system.
+The basis of synergies is that the generic joint displacement, $q$, can be represented as a function of fewer elements than the number of  DoF of the system.
 $S$ is a vector of weights that determines the amount of motion for an individual joint resulting from a single input.
@@
 In contrast, the authors aim to design a geometry-based synergy control scheme by providing an $S$ matrix such that the finger joints move in unison to produce a cylinder grasp.
-To acheive this geometry-based synergy control scheme, we describe our process for building the commanding infrastructure for R2 to take the inputs of synergy type (e.g.
+To acheive this geometry-based synergy control scheme, the process for building the commanding infrastructure for R2 to take the inputs of synergy type (e.g.
 cylinder) and a single variable (e.g.
-diameter) and calculate the synergy matrix from these two inputs.
+diameter) and calculate the synergy matrix from these two inputs is described.
 The \textit{q} matrix of joint angles will then be passed to the robot to move the fingers joints to the calculated angles.
@@
 
-The first step is to build an initial model for grasping by determining the finger angles for grasps of cylinders of specific diameters that span the size range of objects that might be encountered in the workspace.
-For our application, the chosen diameters for grasped objects were 2.54 cm, 3.81 cm, 5.08 cm, and 7.62 cm.
+The first step was to build an initial model for grasping by determining the finger angles for grasps of cylinders of specific diameters that span the size range of objects that might be encountered in the workspace.
+For this application, the chosen diameters for grasped objects were 2.54 cm, 3.81 cm, 5.08 cm, and 7.62 cm.
 For the program, the objects were considered massless.
@@
 This model performed better than traditional inverse kinematic models because it allowed contact with multiple points on the hand rather than only a single point-of-interest on the end-effector.
-The key features of the R2 hand such as the number of DoFs, finger length, joint rotation frames, and actuation scheme were matched.
+The key features of the R2 hand such as the number of  DoF, finger length, joint rotation frames, and actuation scheme were matched.
 The SyGrasp toolbox did not allow for representation of the R2 hands physical compliance, nor could the geometry of the palm be accurately represented.
 
-The SynGrasp model was then provided a synergy matrix that reflected the R2 hand control scheme and its constraings.
-The Robonaut hand contains 18 movable DoFs but only 12 controllable DoFs.
-The thumb is fully controllable along every DoF and contains two DoFs at the basilar joint with independent controls for angle at the proximal phalanx and distal phalanx.
-The index and middle fingers have 2 rotation DoFs at the metacarpophalangeal joint (MCP), pitch and yaw.
+The SynGrasp model was then provided a synergy matrix that reflected the R2 hand control scheme and its constraints.
+The Robonaut hand contains 18 movable  DoF but only 12 controllable DoF.
+The thumb is fully controllable along every DoF and contains two DoF at the basilar joint with independent controls for angle at the proximal phalanx and distal phalanx.
+The index and middle fingers have two rotation  DoF at the metacarpophalangeal joint (MCP), pitch and yaw.
 The proximal (PIP) and distal (DIP) interphalangeal joints are underactuated such that they move at matching angles.
 The ring and little fingers only take a single input value that controls pitch in all three joints (MCP, PIP, and DIP).
-These two fingers have no yawing DoF at the MCP.
+These two fingers have no yaw DoF at the MCP.
 
@@
 All fingers were fully extended in the starting position.
-The object's placement along the palm was varied from near the base of the fingers to the base of the thumb.
+The object's placement along the palm was varied from near the base of the fingers to the base of the thumb, approximately 5cm.
 This allowed testing of uncertainty in position that will be present when the object must be localized.
 Then, the robot was commanded to close its hand based on the synergy values, lift the object, rotate the object upside down, return it to straight, and finally, release it back on the table.
-Successful completion of this set of motions demonstrates a firm grasp on the object through a large motion of the robot.
-
-\begin{figure}[]
-  \centering
-  \includegraphics[width=\linewidth]{manipulation}
-  \caption{Manipulation action taken by R2 to determine successful grasps}
-  \label{testing}
-\end{figure}
+Successful completion of this set of motions demonstrates a firm grasp on the object through a large motion of the robot as shown in Fig \ref{testing}.
 
@@
 The maximum polynomial order used was three.
-The resulting relationships between joint angles and object diameters were relatively simple, which  makes sense; as the object gets larger, the hand opens more.
+The resulting relationships between joint angles and object diameters were relatively simple, which makes sense.
+As the object gets larger, the hand opens more.
 The thumb is the only digit which changed orientations substantially as the diameters got larger as it has more DoF to move into a suitable position.
@@
 \subsection{Testing Protocol}
-After adjusting the grasp models and generating the joint angle fits to data for the four cylindrical validation objects, fifteen objects typically picked up with a cylindrical grasp were manipulated using the R2 hand and the SynGrasp geometrical synergy grasping model.
+After adjusting the grasp models and generating the joint angle fits to data for the four cylindrical validation objects, fifteen objects typically manipulated using a cylindrical grasp were grasped using the R2 hand and the SynGrasp geometrical synergy grasping model.
 These objects ranged from 2.79 to 8.4 cm in diameter and 5 g to 1.02 kg in mass.
-In addition, five non-cylindrical objects were manipulated using the same action illustrated in \ref{thumb_fits}.
+In addition, five non-cylindrical objects were manipulated using the same action illustrated in Fig \ref{thumb_fits}.
 These objects included four shapes resembling rectangular prisms and one hand drill.
-For a grasp to be considered successfull, the object needed to be successfully held by R2, lifted from a table top and be held without slipping as it was rotated by the robot as shown in Fig.
+For a grasp to be considered successful, the object needed to be grasped by R2, lifted from a table top and held without slipping as it was rotated by the robot as shown in Fig.
 \ref{testing}.
+
+\begin{figure}[!b]
+ \centering
+ \includegraphics[width=\linewidth]{manipulation}
+ \caption{Manipulation action taken by R2 to determine successful grasps}
+ \label{testing}
+\end{figure}
 
@@
 
-\begin{figure*}[!b]
+\begin{figure*}[t]
  \centering
@@
  \caption{Results from cylindrical synergy testing using the developed curve fits.
-The blue field contains cylindrical objects.
-The orange contains rectangular prisms, and the yellow contains the complex geometry object, the drill}
+The top three rows contain cylindrical objects.
+The bottom row contains non-cylindrical objects, and the bottom right cell contains the complex geometry object, the drill}
  \label{objects} 
@@
 Due to a redundant DoF, the 4 DoF thumb has many possible locations in which it could contact the cylinder in SynGrasp. 
-This resulted in non-ideal thumb location choices near 7.62 cm diameter.
+This resulted in non-ideal thumb location choices for objects with diameters larger than about 7.6 cm.
 Primarily, the thumb would roll too close to the palm, giving a point contact on the thumb pad rather than a wrap around the cylinder.
@@
 The index and middle finger positions generated by SynGrasp were able to be used with no modifications.
-Overall, the initial joint angles generated by the SynGrasp model resulted in successful grasps of the test objects in a majority of cases, demonstrating the useflness of the methodology.
+Overall, the initial joint angles generated by the SynGrasp model resulted in successful grasps of the test objects in a majority of cases, demonstrating the usefulness of the methodology.
 
-A result from the grasping tests was that cylindrical objects with diameters near 10 cm were grasped by the robot in a pinch grasp fashion.
+A result from the grasping tests was that cylindrical objects with diameters over 10 cm were grasped by the robot in a pinch grasp fashion.
 Future refinements of this geometric-based synergy scheme might explore alternative strategies for larger objects.
-Also, the geometric synergy method was unable to handle the complex geometry of the drill, which demonstrates that while the synergy concept is useful, it is not directly applicable to all.
+Also, the geometric synergy method was unable to handle the complex geometry of the drill, which demonstrates that while the synergy concept is useful, it is not directly applicable to all object types.
 Typical manipulation of this tool has the index finger extended, allowing the other fingers to wrap underneath using the synergy-based cylinder grasp values.
@@
 The combination of these two synergies could create the Dewalt drill grasp and actuation motions in the same framework.
-This is a concept the authors are leaving for future work.
+This concept has been left for future work.
 
@@
 The geometric-based synergy model successfully manipulated all of the cylindrical objects presented in the experiment, demonstrating the usefulness of the concept in practice.
-The testing also highlighted the further abstraction of the grasp for a cylinder synergy four prismatic objects that could be approximated as cylindersto.
+The testing also highlighted the further abstraction of the grasp for a cylinder synergy by manipulating four prismatic objects that could be approximated as cylinders.
 Finally, it was demonstrated that while this synergy is useful for cylinders, other methods are still necessary for complex manipulations like that of a drill.
@@
 Of the 15 cylindrical objects manipulated by the robot, two failures occured.
-In one case, the diameter of the object (hammer) was at he low end of the range tested.
+In one case, the diameter of the object (hammer) was at the low end of the range tested.
 Even with a complete closure grasp, the hammer slid in the grasp, but was not dropped.
@@
 In the second failure, the robot was unable to manipulate the large flashlight without dropping it.
-While the fingers were positioned in an appropriate orientation relative to the object, the weight of the object (~1kg, heaviest of the set tested) and friction between between the glove and object appeared to be the root cause of the failure.
+While the fingers were positioned in an appropriate orientation relative to the object, the weight of the object (1kg, the heaviest of the set tested) and friction between between the glove and object appeared to be the root cause of the failure.
 In practice, the Cutkosky grasp plus affordance template method of grasp designed for the hammer and flashlight for the specific object geometry resulted in the same failures.
@@
 
-The authors demonstrated a novel concept to modify the postural synergy framework developed in neuroscience into an intuitive commanding strategy for high DoF, position controlled robot hands that parameterizes the object to be grasped.
+The authors demonstrated a novel concept to modify the postural synergy framework developed in neuroscience into an intuitive commanding strategy for high DoF position controlled robot hands that parameterizes the object to be grasped.
 The creation of a geometric synergy based on the diameter of a cylindrical object allowed cylinders of varying sizes to be effectively grasped via a single command input.
-The results of this test suggest that this concept could be used to quickly broaden the library of objects the robot can manipulate from a small, specialized set, into a nearly infinite library of manipulatable cylinders and other common shapes.
+The results of this test suggest that this concept could be used to quickly broaden the library of objects the robot can manipulate from a small, specialized set into a nearly infinite library of cylinders and other common shapes.
 

### 2017-10-31 draft_springer_2.tex
edited for spelling and grammar

@@
 The key features of the R2 hand such as the number of  DoF, finger length, joint rotation frames, and actuation scheme were matched.
-The SyGrasp toolbox did not allow for representation of the R2 hands physical compliance, nor could the geometry of the palm be accurately represented.
+The SynGrasp toolbox did not allow for representation of the R2 hands physical compliance, nor could the geometry of the palm be accurately represented.
 
@@
 All fingers were fully extended in the starting position.
-The object's placement along the palm was varied from near the base of the fingers to the base of the thumb, approximately 5cm.
+The object's placement along the palm was varied from near the base of the fingers to the base of the thumb, approximately 5 cm.
 This allowed testing of uncertainty in position that will be present when the object must be localized.
@@
 These objects ranged from 2.79 to 8.4 cm in diameter and 5 g to 1.02 kg in mass.
-In addition, five non-cylindrical objects were manipulated using the same action illustrated in Fig \ref{thumb_fits}.
+In addition, five non-cylindrical objects were manipulated using the same action illustrated in Fig \ref{testing}.
 These objects included four shapes resembling rectangular prisms and one hand drill.

### 2017-10-31 draft_springer_2.tex
abstract edit from O'Malley

@@
 There exists a need for an efficient method to command high degree-of-freedom (DoF) position-controlled dexterous manipulators to grasp a range of objects such that explicit models are not needed for every interaction.
-The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoF to match intuitive measurements of an object to be grasped, which the authors term geometrical synergies.
-Rather than testing the postural synergies that come from the principal components of human grasps, a grasping synergy based on the object to be grasped was designed.
+The authors propose a method termed geometrical synergies that, similar to the neuroscience concept of postural synergies, aims to decrease the commanded DoF of the humanoid hand.
+In the geometrical synergy approach, the method relies on grasp design based on intuitive measurements of the object to be grasped, in contrast to postural synergy methods that focus on the principal components of human grasps to determine robot hand joint commands.
 For this paper, a synergy was designed to grasp cylinder-shaped objects.
@@
 R2's command structure centers around the concept of multi-loop control with a series of embedded loops \cite{r2_control}.
-The lowest level of control is a current loop, wrapped by a velocity loop, wrapped by a torque loop, and finally wrapped by a position loop that specified the desired joint poses.
+The lowest level of control is a current loop, wrapped by a velocity loop, wrapped by a torque loop, and finally wrapped by a position loop that specifies the desired joint poses.
 Because the actuators that position R2's fingers are not series-elastic and have no direct torque measurement capability, the control structure of the R2 hand is modified compared to that used for the series elastic joints in the arms and legs.
